\begin{enumerate}
\item
  \textbf{Question}\\
  Two treatments are being tested against Covid-19. Treatment \(A\) has
  an effectiveness of 90 \% while treatment \(B\) has an effectiveness
  of 70 \%. It has also been found that in 5\% of the patients affected
  by Covid-19 neither of the two treatments is effective.

  \begin{enumerate}
  \item
    Compute the probability that for a patient with Covid-19 only
    treatment \(A\) is effective.
  \item
    What is the probability that treatment \(B\) is effective if \(A\)
    was not effective for a Covid-19 patient?
  \item
    Are independent the two treatments?
  \item
    Compute the probability that in a sample of 6 Covid-19 patients the
    treatment \(A\) is effective in at least 4 of them.
  \item
    Compute the probability that in a sample of 100 Covid-19 patients
    there are less than 3 where none of the treatments are effective.
  \item
    Compute the probability that in a sample of 5 Covid-19 patients some
    of the treatments is effective in at least 3 of them.
  \end{enumerate}

  \textbf{Solution}\\
\item
  \textbf{Question}\\
  The Human chorionic gonadotropin (hCG) hormone is used to detect the
  pregancy during the first weeks of the gestation. A test diagnose the
  pregnancy when the level of hCG is above 12 mUI/ml. Knowing that the
  concentration of hCG in non-pregnant females follows a normal
  probability distribution with mean 5 mUI/ml and standard deviation 2
  mUI/ml, while in pregnant females follows a normal probability
  distribution with mean 25 mUI/ml and standard deviation 5 mUI/ml:

  \begin{enumerate}
  \item
    Compute the percentage of pregnant females with a level of hCG
    between 15 and 20 mUI/ml.
  \item
    Above what level of hCG are the 1\% of non-pregnant females?
  \item
    Compute the sensitiviy and the specificity of the test.
  \item
    If there are 0.5\% of pregnant females in a population, what is the
    percentage of false positives for the test? And the percentage of
    false negatives?
  \end{enumerate}

  \textbf{Solution}\\
\end{enumerate}
