\begin{enumerate}
\item
  \textbf{Question}\\
  The table below summarizes the time (in minutes) required to remove
  anesthesia after a surgery in a sample of 50 patients.

  \[% latex table generated in R 3.6.2 by xtable 1.8-4 package
  % Fri Jan 10 12:29:15 2020
  \begin{array}{cr}
   \mbox{Time} & \mbox{Patients} \\ 
    \hline
  10-30 & 2 \\ 
    30-45 & 11 \\ 
    45-60 & 18 \\ 
    60-90 & 9 \\ 
    90-120 & 8 \\ 
    120-180 & 2 \\ 
     \hline
  \end{array}\]

  \begin{enumerate}
  \item
    Are there some outliers in the sample?
  \item
    Compute the mean. Is it representative?
  \item
    If according to a postoperative protocol the 15\% of patients that
    require more time to remove the anesthesia must be monitored, above
    what time should a patient be monitored?
  \item
    If we apply a drug that is anesthesia antagonist, it is known that
    the time required to remove the anesthesia decreases a 25\%. How
    will the time decrease affect the representativeness of the mean?
  \item
    If it is known that another type of anesthesia \(B\) has mean 50
    minutes and standard deviation 15 minutes, what time is relatively
    greater, 70 minutes with this type of anesthesia or 60 minutes with
    the type \(B\)?.
  \end{enumerate}

  Use the following sums for the computations: \(\sum x_in_i=3212.5\)
  min, \(\sum x_i^2n_i=249706.25\) min\(^2\),
  \(\sum (x_i-\bar x)^3n_i=1400531.25\) min\(^3\) y
  \(\sum (x_i-\bar x)^4n_i=143958437.7\) min\(^4\).\\
  \textbf{Solution}\\

  \begin{enumerate}
  \item
    \(Q_1=44.3182\), \(Q_3=81.6667\), \(IQR=37.3485\), \(f_1=-11.7045\)
    and \(f_2=137.6894\). Since the last class contains values above the
    upper fence, there could be outliers.
  \item
    \(\bar x=64.25\) min, \(s^2=866.0625\) min\(^2\), \(s=29.4289\) min
    and \(cv=0.458\) Thus the representativity of the mean is moderate.
  \item
    \(P_{85}=99.375\) min.
  \item
    Applying the linear transformation \(y=0.75x\), \(\bar y=48.1875\)
    min, \(s_y=22.0717\) min and \(cv=0.458\). Thus the representativity
    of the mean is the same.
  \item
    Standard score in first anesthesia: \(z(70)=0.1954\).\\
    Standard score in anesthesia \(B\): \(z(60)=0.6667\).\\
    Thus, 60 min with anesthesia \(B\) is relatively greater.
  \end{enumerate}
\item
  \textbf{Question}\\
  The table below summarizes the scores of a group of 10 students in
  three practical exams of Maths.
  \[% latex table generated in R 3.6.2 by xtable 1.8-4 package
  % Fri Jan 10 12:29:15 2020
  \begin{array}{rrr}
   \mbox{Exam 1} (X) & \mbox{Exam 2} (Y) & \mbox{Exam 3} (Z) \\ 
    \hline
  5.5 & 3.2 & 5.0 \\ 
    7.5 & 6.5 & 2.0 \\ 
    2.5 & 4.0 & 1.0 \\ 
    6.0 & 4.0 & 6.0 \\ 
    8.0 & 7.5 & 6.0 \\ 
    4.0 & 3.5 & 1.0 \\ 
    7.0 & 5.5 & 4.0 \\ 
    9.5 & 10.0 & 9.0 \\ 
    10.0 & 9.5 & 8.0 \\ 
    1.0 & 3.0 & 0.5 \\ 
     \hline
  \end{array}\]

  \begin{enumerate}
  \item
    Which two scores are more linearly correlated?
  \item
    Using linear models, what are the expected scores of the second and
    third exams for a student with a score \(6.5\) in the first exam?
  \end{enumerate}

  Use the following sums for the computations:\\
  \(\sum x_i=61\), \(\sum y_i=56.7\), \(\sum z_i=42.5\),\\
  \(\sum x_i^2=449\), \(\sum y_i^2=382.49\), \(\sum z_i^2=264.25\),\\
  \(\sum x_iy_j=405.85\), \(\sum x_iz_j=327\), \(\sum y_jz_j=295\).

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    \(\bar x=6.1\), \(s_x^2=7.69\),\\
    \(\bar y=5.67\), \(s_y^2=6.1001\),\\
    \(\bar z=4.25\), \(s_z^2=8.3625\),\\
    \(s_{xy}=5.998\), \(s_{xz}=6.775\), \(s_{yz}=5.4025\),\\
    \(r^2_{xy}=0.7669\), \(r^2_{xz}=0.7138\) and \(r^2_{yz}=0.5722\).\\
    Thus, the two variables more linearly related are \(X\) and \(Y\),
    since their coefficient of determination is greater.
  \item
    Regression line of \(Y\) on \(X\): \(y=0.9122 + 0.78x\) and
    \(y(6.5)=5.982\).\\
    Regression line of \(Z\) on \(X\): \(z=-1.1242 + 0.881x\) and
    \(z(6.5)=4.6024\).
  \end{enumerate}
\end{enumerate}
