\begin{enumerate}
\item
  \textbf{Question}\\
  The time required by a drug \(A\) to be effective has been measured
  (in minutes) in a sample of 150 patients. The table below summarize
  the results.

  \[% latex table generated in R 4.1.3 by xtable 1.8-4 package
  % Thu Mar 24 10:00:35 2022
  \begin{array}{lr}
   \mbox{Response time} & \mbox{Patients} \\ 
    \hline
  (0,5] & 5 \\ 
    (5,10] & 15 \\ 
    (10,15] & 32 \\ 
    (15,20] & 36 \\ 
    (20,30] & 42 \\ 
    (30,60] & 20 \\ 
     \hline
  \end{array}\]

  \begin{enumerate}
  \item
    Are there outliers in the sample? Justify the answer.
  \item
    What is the minimum time for the 20\% of patients with highest
    response time?
  \item
    What is the average response time? Is the mean representative?
  \item
    Can we assume that the sample comes from a normal population?
  \item
    If we take another sample of patients with mean 18 min and standard
    deviation 15 min, in which group is greater a response time of 25
    min?
  \end{enumerate}

  Use the following sums for the computations: \(\sum x_i=3105\) min,
  \(\sum x_i^2=83650\) min\(^2\), \(\sum (x_i-\bar x)^3=206851.65\)
  min\(^3\) y \(\sum (x_i-\bar x)^4=8140374.96\) min\(^4\).

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    \(Q_1=12.7344\) min, \(Q_3=25.8333\) min, \(IQR=13.099\) min,
    \(f_1=-6.9141\) min and \(f_2=45.4818\) min. Therefore there are
    outliers in the sample since the upper limit of the last interval is
    above the upper fence.
  \item
    \(P_{80}=27.619\) min.
  \item
    \(\bar x=20.7\) min, \(s^2=129.1767\) min\(^2\), \(s=11.3656\) min
    and \(cv=0.5491\). The mean is not very representative since the
    \(cv>0.5\).
  \item
    \(g_1=0.9393\) and \(g_2=0.2523\). Since \(g_1\) and \(g_2\) are
    between -2 and 2, we can assumme that the sample comes from a normal
    (bell-shaped) population.
  \item
    The standard score of the first sample is \(z(25)=0.3783\) and the
    standard score of the second one \(z(25)=0.4667\), thus a time of 25
    min is relatively greater in the second sample.
  \end{enumerate}
\item
  \textbf{Question}\\
  We have measured the average number of weekly hours of study \(X\) and
  the score in a clinic entrance test \(Y\) of 8 candidates, getting the
  following results:

  \(\sum x_i=15.9\), \(\sum \log(x_i)=3.852\), \(\sum y_j=41.5\),
  \(\sum \log(y_j)=11.511\),\\
  \(\sum x_i^2=42.23\), \(\sum \log(x_i)^2=5.559\),
  \(\sum y_j^2=274.25\), \(\sum \log(y_j)^2=20.742\),\\
  \(\sum x_iy_j=103.3\), \(\sum x_i\log(y_j)=28.047\),
  \(\sum \log(x_i)y_j=32.616\).

  \begin{enumerate}
  \item
    Compute the equations of the logarithmic and exponential regression
    models of the score as a function of the average number of hours of
    study.
  \item
    Use the best of the previous models to predict the score for
    somebody that study \(3.2\) hours a week.
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    \(\bar x=1.9875\) hours, \(s_x^2=1.3286\) hours\(^2\).\\
    \(\overline{\log(x)}=0.4815\) log(hours), \(s_{\log(x)}^2=0.463\)
    log(hours)\(^2\).\\
    \(\bar y=5.1875\) points, \(s_y^2=7.3711\) points\(^2\).\\
    \(\overline{\log(y)}=1.4389\) log(points), \(s_{\log(y)}^2=0.5224\)
    log(points)\(^2\).\\
    \(s_{x\log(y)}=0.6461\), \(s_{\log(x)y}=1.5792\)\\
    Logarithmic regression model: \(y=3.5453+3.4106\log(x)\)\\
    Exponential regression model: \(y=e^{0.4723+0.4863x}\)
  \item
    Logarithmic coefficient of determination: \(r^2=0.7307\)\\
    Exponential coefficient of determination: \(r^2=0.6015\)\\
    Therefore, the best regression model to predict is the
    exponential.\\
    Prediction: \(y(3.2)=14.4592\).
  \end{enumerate}
\end{enumerate}
