\begin{enumerate}
\item
  \textbf{Question}\\
  Laetisaric acid is a compound that can be used to control fungal
  diseases in some plantations. The table below shows the radial growth
  (in cm) of the fungus Pleurotus ostreatus exposed to different
  concentrations of laetisaric acid (ing mg/l).

  \[% latex table generated in R 4.0.3 by xtable 1.8-4 package
  % Sun Feb  7 21:59:15 2021
  \begin{array}{lrrrrrrrrrrrr}
     \hline
  \mbox{Laetisaric acid (mg/l)} & 0.0 & 0 & 3.0 & 3.0 & 6 & 6 & 10.0 & 10.0 & 20.0 & 20.0 & 30.0 & 30 \\ 
    \mbox{Fungus growth (cm)} & 33.3 & 31 & 29.8 & 27.8 & 28 & 29 & 25.5 & 23.8 & 18.3 & 15.5 & 11.7 & 10 \\ 
     \hline
  \end{array}\]

  \begin{enumerate}
  \item
    Compute the equation of the regression line that best explains
    fungal growth as a function of acid concentration.
  \item
    Compute the linear correlation and determination coefficients and
    interpret them.
  \item
    How much does the fungal population increase or decrease for each
    one mg/dl increment in acid concentration?
  \item
    What are the expected fungal growths for acid concentrations of 20
    and 200 mg/l? Which of these predictions is more reliable?
  \end{enumerate}

  Use the following sums for the computations: \(\sum x_i=138\) mg/l,
  \(\sum y_i=283.7\) cm, \(\sum x_i^2=2890\) (mg/l)\(^2\),
  \(\sum y_i^2=7384.49\) cm\(^2\) and \(\sum x_iy_j=2334.8\)
  mg/l\(\cdot\) cm.

  \textbf{Solution}\\
\item
  \textbf{Question}\\
  The table below shows the blood uric acid concentration of 8 men and
  10 women in mg/dl.

  \[% latex table generated in R 4.0.3 by xtable 1.8-4 package
  % Sun Feb  7 21:59:15 2021
  \begin{array}{lrrrrrrrrrr}
     \hline
  \mbox{Men ($X$)} & 4.7 & 3.6 & 5.2 & 6.8 & 9.5 & 4.8 & 5.6 & 5.4 &  &  \\ 
    \mbox{Women ($Y$)} & 3.2 & 4.5 & 5.4 & 2.1 & 6.7 & 5.2 & 3.8 & 4.3 & 7.2 & 2.6 \\ 
     \hline
  \end{array}\]

  Se pide:

  \begin{enumerate}
  \item
    In which group, men or women, is the mean more representative?
  \item
    In which group, men or women, is the uric acid distribucion more
    simmetric?
  \item
    In which group, men or women, is the uric acid distribution flatter?
  \item
    Can we assume that the uric acid sample from women comes from a
    normal population?
  \item
    What uric acid concentration must a woman have to be relative higher
    than 6 mg/dl in a man?
  \item
    If all the values of the variable \(X\) are multiplied by a number,
    what must that number be to make the mean of the new variable as
    representative as the mean of \(Y\)?
  \end{enumerate}

  Use the following sums for the computations:\\
  Hombres: \(\sum x_i=45.6\) mg/dl, \(\sum x_i^2=282.14\) (mg/dl)\(^2\),
  \(\sum (x_i-\bar x)^3=45.06\) (mg/dl)\(^3\) and
  \(\sum (x_i-\bar x)^4=231.15\) (mg/dl)\(^4\).\\
  Mujeres: \(\sum y_i=45\) mg/dl, \(\sum y_i^2=227.52\) (mg/dl)\(^2\),
  \(\sum (y_i-\bar y)^3=8.17\) (mg/dl)\(^3\) and
  \(\sum (y_i-\bar y)^4=126.77\) (mg/dl)\(^4\).\\
  \textbf{Solution}\\
\end{enumerate}
