\begin{enumerate}
\item
  \textbf{Question}\\
  It has been observed that the concentration of a metabolite in urine
  can be used as a diagnostic test for a disease. The concentration (in
  mg/dl) in healthy individuals follows a normal distribution with mean
  90 and standard deviation 8, while in sick individuals follows a
  normal distribution with mean 120 and standard deviation 10.

  \begin{enumerate}
  \item
    If the cut-off point is set at 105 mg/dl (positive above and
    negative below), what is the sensitivity and the specificity of the
    test?
  \item
    If the cut-off point is set at 105 mg/dl and we assume a prevalence
    of 10\%, what is the probability of a correct diagnostic?
  \item
    If we want a sensitivity of 95\%, where must we set the cut-off
    point? What would the specificity of the test be ?
  \end{enumerate}

  \textbf{Solution}\\
  Let \(X\) and \(Y\) be the distributions of the concentration of
  metabolitte in healthy and sick individuals respectively.

  \begin{enumerate}
  \item
    Sensitivity: \(P(+|D) = P(Y>105) = 0.9332\).\\
    Specificity: \(P(-|\overline D) = P(X<105) = 0.9696\).
  \item
    \(P(\mbox{correct diagnostic}) = P(D\cap +) + P(\overline D \cap -) = 0.966\).
  \item
    Cut-off point \(103.5515\) mg/dl.\\
    Specificity: \(P(-|\overline D) = P(X<103.5515) = 0.9549\).
  \end{enumerate}
\item
  \textbf{Question}\\
  Let \(A\) and \(B\) be two events of a random experiment, such that
  \(A\) is three times as likely as \(B\), \(P(A\cup B)=0.8\) and
  \(P(A\cap B)=0.2\).

  \begin{enumerate}
  \item
    Compute \(P(A)\) and \(P(B)\).
  \item
    Compute \(P(A-B)\) and \(P(B-A)\).
  \item
    Compute \(P(\bar A \cup \bar B)\) and \(P(\bar A \cap \bar B)\).
  \item
    Compute \(P(A|B)\) and \(P(B|A)\).
  \item
    Are \(A\) and \(B\) independent?
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    \(P(A) = 0.75\) and \(P(B) = 0.25\).
  \item
    \(P(A-B) = 0.55\) and \(P(B-A) = 0.05\).
  \item
    \(P(\bar A \cup \bar B) = 0.8\) and \(P(\bar A \cap \bar B) = 0.2\).
  \item
    \(P(A|B) = 0.8\) and \(P(B|A) = 0.2667\).
  \item
    No, they are dependent since \(P(A|B)\neq P(A)\).
  \end{enumerate}
\item
  \textbf{Question}\\
  The employees of a courier company send an average of \(246.2\)
  messages in a period of 12 hours. It is also known that the mean of
  messages sent by males is \(256.2\) and by females is \(237.4\) in the
  same period.

  \begin{enumerate}
  \item
    Compute the probability that a random person of the company sends 5
    messages in a period of half an hour.
  \item
    If we draw randomly 10 women of this company, what is the
    probability that at least 3 of them sends more than one message in a
    period of one hour?
  \item
    If we draw randomly 100 men of this company, what is the probability
    that none of them sends less than 2 messages in a period of a
    quarter of an hour?
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    Let \(X\) be the number of messages sent in 1 hour. Then
    \(X\sim P(10.2583)\) and \(P(X=5)=0.0332\).
  \item
    Let \(Y\) be the number of women in a sample of 10 that sent more
    than 1 message in 1 hour. Then \(Y\sim B(10, 1)\) and
    \(P(Y\geq 3)=1\).
  \item
    Let \(Z\) be the number of men in a sample of 100 that sent less
    than 2 messages in a quarter of hour. Then \(Z\sim B(100, 0.0305)\)
    and \(P(Z=0)=0.0166\).
  \end{enumerate}
\end{enumerate}
