\begin{enumerate}
\item
  \textbf{Question}\\
  An ultrasonic technique is used to diagnose a disease with a
  sensitivity of 91\% and a specificity of 98\%. The prevalence of the
  disease is 20\%,

  \begin{enumerate}
  \item
    If we apply the technique to an individual and the outcome is
    positive, what is the probability of having the disease for that
    individual?
  \item
    If the outcome was negative, what is the probability of not having
    the disease?
  \item
    Is this technique more reliable to confirm or to rule out the
    disease? Justify the answer.
  \item
    Compute the probability of having a correct diagnose with this
    technique.
  \end{enumerate}

  \textbf{Solution}\\
  Let \(D\) the event corresponding to have the disease and + and - the
  events corresponding to have a positive and negative outcome
  respectively in the test.

  \begin{enumerate}
  \item
    \(PPV=0.9192\).
  \item
    \(NPV=0.9776\).
  \item
    It is more reliable to rule out the disease since the NPV is greater
    than the PPV.
  \item
    \(P(D\cap +)+P(\overline D\cap -) = 0.966\).
  \end{enumerate}
\item
  \textbf{Question}\\
  It is known that the femur length of a fetus with 25 weeks of
  pregnancy follows a normal distribution with mean 44 mm and standard
  deviation 2 mm.

  \begin{enumerate}
  \item
    Compute the probability that the femur length of a fetus with 25
    weeks is greater than 46 mm.
  \item
    Compute the probability that the femur lenght of a fetus with 25
    weeks is between 46 and 49 mm.
  \item
    Compute an interval \((a,b)\) centered at the mean, such that it
    contains 80\% of the femur lengths of fetus with 25 weeks.
  \end{enumerate}

  \textbf{Solution}\\
  Let \(X\sim N(44,2)\) be the femur length of fetus with 25 weeks of
  pregnancy.

  \begin{enumerate}
  \item
    \(P(X>46)=0.1587\).
  \item
    \(P(46<X<49))=0.1524\).
  \item
    The interval centered at \(44\) that contains 80\% of the femur
    lengths of fetus with 25 weeks is \((41.4369,46.5631)\).
  \end{enumerate}
\item
  \textbf{Question}\\
  The probability that an injury \(A\) is repeated is \(4/5\), the
  probability that another injury \(B\) is repeated is \(1/2\), and the
  probability that none of them are repeated is \(1/20\). Compute the
  probability of the following events:

  \begin{enumerate}
  \item
    At least one injury is repeated.
  \item
    Only injury \(B\) is repeated.
  \item
    Injury \(B\) is repeated if injury \(A\) has been repeated.
  \item
    Injury \(B\) is repeated if injury \(A\) has not been repeated.
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    \(P(A\cup B)=19/20\).
  \item
    \(P(B\cap\overline{A})=3/20\).
  \item
    \(P(B/A)=7/16\).
  \item
    \(P(B/\overline{A})=3/4\).
  \end{enumerate}
\item
  \textbf{Question}\\
  A physical therapy clinic opens 6 hours a day and the average number
  of patients that arrive to the clinic is 12 a day.

  \begin{enumerate}
  \item
    Compute the probability of arriving more than 4 patients in 1 hours.
  \item
    If the clinic has 4 physiotherapists and each of them can treat one
    patient per hour, what is the probability that a day there was some
    hour in which some patient can not be attended? How many
    physiotherapists must be in the clinic to guarantee that this
    probability is less than 10\%?
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    Let \(X\) be the number of patients that arrive in 1 hours.
    \(X\sim P(2)\) and \(P(X>4)=0.0527\).
  \item
    Let \(Y\) be the number of hours in a day in which some patient can
    not be treated. \(Y\sim B(6, 0.0527)\) and \(P(Y>0)=0.2771\).\\
    The clinic requires 5 phisiotherapists, since \(P(X>5)=0.0527\) and
    \(P(Y>0)=0.0954\), with \(Y\sim B(6, 0.0166)\) now.
  \end{enumerate}
\end{enumerate}
