\begin{enumerate}
\item
  \textbf{Question}\\
  A test to detect the COVID19 was applied to 850 persons infected by
  COVID19 with a positive outcome in 800 of them, and it was also
  applied to 9150 non-infected persons with a positive outcome in 10\%
  of them.

  \begin{enumerate}
  \item
    Compute the sensitivity and the specificity of the test.
  \item
    Compute the positive and the negative predictive values and
    interpret them.
  \item
    Compute the probability of a correct diagnostic.
  \end{enumerate}

  \textbf{Solution}\\
  Let \(D\) the event corresponding to suffering COVID19 and \(+\) and
  \(-\) the events corresponding to get a positive and a negative
  outcome respectively.

  \begin{enumerate}
  \item
    The sensitivity is \(P(+|D) = 0.9412\) and specificity
    \(P(-|\overline D) = 0.9\).
  \item
    Positive predictive value \(P(D|+) = 0.4665\) and negative
    predictive value \(P(\overline D|-) = 0.994\). As de positive
    predictive value is less than 0.5 we can not use this test to
    confirm COVID19, but we can use it to rule it out with a strong
    confidence since the negative predictive value is pretty close to 1.
  \item
    \(P(D\cap +) + P(\overline D\cap -) = 0.9035\).
  \end{enumerate}
\item
  \textbf{Question}\\
  A newborn baby affected by Moebius syndrome blinks, on average, twice
  a minute.

  \begin{enumerate}
  \item
    Compute the probability that a newborn blinks twice in half a
    minute.
  \item
    In a hospital five children have been born with Moebius syndrome.
    Compute the probability that at least 3 of them blink in their first
    minute of life.
  \item
    In which distribution is more representative the mean, in the number
    of times that a newborn blinks in a minute or in the number of times
    that a newborn blinks in half a minute?
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    Let \(X\) be the number of times that a newborn blinks in half a
    minute, then \(X\sim P(1)\) and \(P(X=2)=0.1839\).
  \item
    Let \(Y\) be the number of newborns that blink in their first minute
    of life in a sample of 5 newborns, then \(Y\sim B(5, 0.8647)\) and
    \(P(Y\geq 3)=0.98\).
  \item
    Let \(Z\) be the number of times that a newborn blinks in a minute,
    then \(cv_z = 0.7071\) and \(cv_x = 1\). Thus, the mean of \(Z\)
    represents better since its coefficient of variation is smaller.
  \end{enumerate}
\item
  \textbf{Question}\\
  The prolactin level in pregnant and non-pregnant females follows a
  normal distribution with different means but with the same variance.
  When the prolactin levels exceed 15 ng/ml, females secrete milk
  through their mammary glands. It is known that 95\% of pregnant
  females secrete milk but only 1\% of non-pregnant females secret milk.

  \begin{enumerate}
  \item
    If the median of the prolactin level in pregnant females is 16
    ng/ml, what are the means and the standard deviation of the
    prolactin level in both populations?\\
    Remark: If you are not able to compute the mean or the standard
    deviation for pregnant females, use \(\mu=17\) ng/ml and
    \(\sigma=2\) ng/ml for the next parts.
  \item
    Compute the percentage of pregnant females with a prolactin level
    between 15.5 and 17 ng/ml.
  \item
    Compute the prolactin level such that 20\% of pregnant females are
    above that level.
  \end{enumerate}

  \textbf{Solution}\\
  Let \(X\) and \(Y\) be the prolactin levels in pregnant and
  non-pregnan females respectively.

  \begin{enumerate}
  \item
    \(\mu_x=16\) ng/ml, \(\mu_y=13.5857\) ng/ml and \(\sigma=0.608\)
    ng/ml.
  \item
    \(P(15.5<X<17) = 0.7446\), so 74.4583\% of pregnant females.
  \item
    \(P_{80} = 16.5117\) ng/ml.
  \end{enumerate}
\item
  \textbf{Question}\\
  An organism has the same chance of being infected by a virus and a
  bacteria. At the same time, the probability of being infected by a
  virus doubles when the organism has been previously infected by a
  bacteria. On the other hand, the probability of being infected by no
  pathogen (neither virus nor bacteria) is \(0.52\).

  \begin{enumerate}
  \item
    What is the probability of being infected by a virus and a bacteria
    at the same time?
  \item
    What is the probability of being infected by a bacteria if it has
    been infected by a virus?
  \item
    What is the probability of being infected only by a virus?
  \item
    Are the events of being infected by a virus an a bacteria
    independent?
  \end{enumerate}

  \textbf{Solution}\\
  Let \(V\) and \(B\) the events corresponding to be infected by a virus
  and a bacteria respectively.

  \begin{enumerate}
  \item
    \(P(V\cap B) = 0.32\).
  \item
    \(P(B|V) = 0.8\).
  \item
    \(P(V\cap \overline B) = 0.08\).
  \item
    The events are dependents since \(P(V) = 0.4 \neq 0.8 = P(V|B)\).
  \end{enumerate}
\end{enumerate}
