\begin{enumerate}
\item
  \textbf{Question}\\
  A study tries to determine the effect of smoking during the pregnancy
  in the weight of newborns. The table below shows the daily number of
  cigarretes smoked by mothers (\(X\)) and the weight of the newborn
  (all of them are males) (\(Y\)).

  \[% latex table generated in R 3.6.0 by xtable 1.8-4 package
  % Wed Jun  5 13:57:18 2019
  \begin{array}{lrrrrrrrrrrrr}
     \hline
  \mbox{Daily num cigarettes} & 10.00 & 14.00 & 8.00 & 11.00 & 7.00 & 6.00 & 2.00 & 5.00 & 9.00 & 9.00 & 4.00 & 6.00 \\ 
    \mbox{Weight (kg)} & 2.55 & 2.44 & 2.68 & 2.65 & 2.71 & 2.85 & 3.45 & 2.93 & 2.67 & 2.59 & 3.02 & 2.72 \\ 
     \hline
  \end{array}\]

  \begin{enumerate}
  \item
    Give the equation of the regression line of the weight of newborns
    on the daily number of cigarettes and interpret the slope.
  \item
    Which regression model is better to predict the weight of newborns,
    the logarithmic or the exponential?
  \item
    Use the best of the two previous regression models to predict the
    weight of a newborn whose mother smokes 12 cigarettes a day. Is this
    prediction reliable?
  \end{enumerate}

  Use the following sums for the computations:\\
  \(\sum x_i=91\) cigarettes, \(\sum \log(x_i)=23.0317\)
  \(\log(\mbox{cigarettes})\), \(\sum y_j=33.26\) kg,
  \(\sum \log(y_j)=12.1857\) \(\log(\mbox{kg})\),\\
  \(\sum x_i^2=809\) cigarettes\(^2\), \(\sum \log(x_i)^2=47.196\)
  \(\log(\mbox{cigarettes})^2\), \(\sum y_j^2=92.9708\) kg\(^2\),
  \(\sum \log(y_j)^2=12.4665\) \(\log(\mbox{kg})^2\),\\
  \(\sum x_iy_j=243.61\) cigarettes\(\cdot\)kg,
  \(\sum x_i\log(y_j)=89.3984\) cigarettes\(\cdot\log(\mbox{kg})\),
  \(\sum \log(x_i)y_j=62.3428\) \(\log(\mbox{cigarettes})\)kg,
  \(\sum \log(x_i)\log(y_j)=22.8753\)
  \(\log(\mbox{cigarettes})\log(\mbox{kg})\).

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    \(\bar x=7.5833\) cigarettes, \(s_x^2=9.9097\) cigarettes\(^2\).\\
    \(\bar y=2.7717\) kg, \(s_y^2=0.0654\) kg\(^2\).\\
    \(s_{xy}=-0.7176.\) cigarettes\(\cdot\)kg\\
    Regression line: \(y=-0.0724x + 3.3208\).
  \item
    \(\overline{\log(x)}=1.9193\) log(cigarettes),
    \(s_{\log(x)}^2=0.2492\) log(cigarettes)\(^2\).\\
    \(\overline{\log(y)}=1.0155\) log(kg), \(s_{\log(y)}^2=0.0077\)
    log(kg)\(^2\).\\
    \(s_{x\log(y)}=-0.2508\) cigarettes\(\cdot\)log(kg),
    \(s_{\log(x)y}=-0.1245\) log(cigarettes)\(\cdot\)kg\\
    Logarithmic coef. determination: \(r^2=0.9499\)\\
    Exponential coef. determination: \(r^2=0.8268\)\\
    Therefore, the logarithmic models fits better the data and is better
    to predict the weight.
  \item
    Logarithmic regression model: \(y=3.7301+-0.4994\log(x)\).\\
    Prediction: \(y(12)=2.4892\) kg. The coefficient of determination is
    high but the sample size small, so the prediction is not enterely
    reliable.
  \end{enumerate}
\item
  \textbf{Question}\\
  The table below summarize the time that took to the runners to reach
  the finish in a long-distance race in Madrid:

  \[% latex table generated in R 3.6.0 by xtable 1.8-4 package
  % Wed Jun  5 13:57:19 2019
  \begin{array}{lr}
   \mbox{Time (min)} & \mbox{Num runners} \\ 
    \hline
  (30,35] & 15 \\ 
    (35,40] & 35 \\ 
    (40,45] & 40 \\ 
    (45,50] & 10 \\ 
     \hline
  \end{array}\]

  In a another race in Paris, the mean of time was 40 minutes, the
  standard deviation 5 minutes and the coeffitient of skewness \(0.75\).

  \begin{enumerate}
  \item
    What percentage of runners took less than 42 minutes to reach the
    finish in Madrid?
  \item
    Compute and interpret the interquartile range of the time for Madrid
    race.
  \item
    In which race the mean of the time is more representative?
  \item
    In which race the time have a more simmetric distribution?
  \item
    In which race a time of 39 minutes to reach the finish is relatively
    smaller?
  \end{enumerate}

  Use the following sums for the computations: \(\sum x_i=3975\) min,
  \(\sum x_i^2=159875\) min\(^2\), \(\sum (x_i-\bar x)^3=-628.12\)
  min\(^3\) y \(\sum (x_i-\bar x)^4=80701.95\) min\(^4\).

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    \(F(42)=0.66\), thus approximately \(66\%\) of runners finished
    before 42 minutes.
  \item
    \(Q_1=36.4286\) min, \(Q_3=43.125\) min, \(IQR=6.6964\) min. The
    central 50\% of times fall in a range of \(6.6964\) minutes.
  \item
    Madrid statistics: \(\bar x=39.75\) min, \(s^2=18.6875\) min\(^2\),
    \(s=4.3229\) min and \(cv=0.1088\).\\
    Paris statistics: \(cv=0.125\). Thus, the mean of time in Madrid is
    a little bit more representative since the coef. of variation is
    smaller.
  \item
    \(g_1=-0.0778\), that is closer to 0 than the distribution of times
    in Paris, thus the distribution of times in Madrid is more
    simmetric.
  \item
    The standard score of the Madrid sample is \(z(39)=-0.1735\) and the
    standard score of the Paris one \(z(39)=-0.2\), thus a time of 39
    min is relatively smaller in the sample of Paris.
  \end{enumerate}
\end{enumerate}
