\begin{enumerate}
\item
  \textbf{Question}\\
  A study tries to determine the effectiveness of an occupational risk
  prevention program in jobs that require to be sit a lot of hours. A
  sample of 500 individuals between 40 and 50 years that spent more than
  5 hours sitting was drawn. Half of the individuals followed the
  prevention program (treatment group) and the other half not (control
  group). After 5 years it was observed that 12 individuals suffered
  spinal injuries in the group following the prevention program while 32
  individuals suffered spinal injuries in the other group. In the
  following 5 years it was observed that 21 individuals suffered spinal
  injuries in the group following the prevention program while 48
  individuals suffered spinal injuries in the other group.

  \begin{enumerate}
  \item
    Compute the cumulative incidence of spinal injuries in the total
    sample after 5 years and after 10 years.
  \item
    Compute the absolute risk of suffering spinal injuries in 10 years
    in the treatment and control groups.
  \item
    Compute the relative risk of suffering spinal injuries in 10 years
    in the treatment group compared to the control group. Interpret it.
  \item
    Compute the odds ratio of suffering spinal injuries in 10 years in
    the treatment group compared to the control group. Interpret it.
  \item
    Which statistics, the relative risk or the odds ratio, is more
    suitable in this study? Justify the answer.
  \end{enumerate}

  \textbf{Solution}\\
  Let \(D\) be the event of suffering spinal injuries.

  \begin{enumerate}
  \item
    Cumulative incidence after 5 years: \(R(D)=0.088\).\\
    Cumulative incidence after 10 years: \(R(D)=0.226\).
  \item
    Risk in the treatment group: \(R_T(D)=0.132\).\\
    Risk in the control group: \(R_C(D)=0.32\).
  \item
    \(RR(D)=0.4125\). Thus, the risk of suffering spinal injuries is
    less than half following the prevention program.
  \item
    \(OR(D)=0.3232\). Thus, the odd of suffering spinal injuries is less
    than one third following the prevention program.
  \item
    Since the study is prospective and we can estimate the prevalence of
    \(D\), both statistics are suitable, but relative risk is easier to
    interpret.
  \end{enumerate}
\item
  \textbf{Question}\\
  The table below shows the results of a study to evaluate the
  usefulness of a reactive strip to diagnose an urinary infection.
  \[\begin{array}{ccc}
  \hline
  \mbox{Outcome} & \mbox{Infection} & \mbox{No infection}\\
  \mbox{Positive} & 60 & 80\\
  \mbox{Negative} & 10 & 200\\
  \hline
  \end{array}\]

  \begin{enumerate}
  \item
    Compute the sensitivity and the specificity of the test.
  \item
    Compute the positive and the negative predictive values. Is this
    test better to confirm or to rule out the infection?
  \item
    If another study has determined that the true prevalence of the
    infection is 2\%, how does this affect to the predictive values?
  \end{enumerate}

  \textbf{Solution}\\
  Let \(D\) be the event corresponding to suffering the urinary
  infection and \(+\) and \(-\) the events corresponding to get a
  positive and negative outcome in the test respectively.

  \begin{enumerate}
  \item
    Sensitivity = \(0.8571\) and Specificity = \(0.7143\).
  \item
    \(PPV=0.4286\) and \(NPV=0.9524\). Since the \(PPV<NPV\) the test is
    better to rule out the infection.
  \item
    \(PPV=0.0577\) and \(NPV=0.9959\). The positive predictive value
    descreases a lot while the negative predictive value increases al
    little bit.
  \end{enumerate}
\item
  \textbf{Question}\\
  The time required to recover from an injury follows a normal
  distribution with variance 64 days. It is also known that 10\% of
  people with this injury require more than 80 days to recover.

  \begin{enumerate}
  \item
    What is the expected time required to recover from the injury?\\
    Remark: Use \(\mu=70\) for the next part if you do not know how to
    compute it.
  \item
    What percentage of individuals will require between 60 and 75 days
    to recover?
  \item
    If we draw a random sample of 12 individuals with this injury, what
    is the probability of having between 9 and 11 individuals, both
    included, requiring less than 80 days to recover?
  \item
    If we draw a random sample of 500 individuals with this injury, what
    is the probability of having less than 4 requiring a time above the
    99th percentile to recover?
  \end{enumerate}

  \textbf{Solution}\\
  Let \(X\) be the time required to recover from the injury. Then
  \(X\sim N(\mu, 8)\).

  \begin{enumerate}
  \item
    \(\mu=69.7476\) days.
  \item
    \(P(60<X<75) = 0.6327\).
  \item
    Let \(Y\) be the number of individuals with the injury requiring
    less than 80 days to recover in a sample of 12. Then
    \(Y\sim B(12, 0.9)\) and \(P(9\leq Y\leq 11)=0.6919\).
  \item
    Let \(Z\) be the number of individuals with the injury requiring a
    time above the 99th percentile to recover in a sample of 500. Then
    \(Z\sim B(500, 0.01)\approx P(5)\) and \(P(Z\leq 4)=0.265\).
  \end{enumerate}
\end{enumerate}
