\begin{enumerate}
\item
  \textbf{Question}\\
  A test to detect prostate cancer produces 1\% of false positives and
  0.2\% false negatives. It is known that 1 in 400 males suffer this
  type of cancer.

  \begin{enumerate}
  \item
    Compute the sensitivity and the specificity of the test.
  \item
    If a male got a positive outcome in the test, what is the chance of
    developing cancer?
  \item
    Compute and interpret the negative predictive value.
  \item
    Is this test better to predict or to rule out the cancer?
  \item
    To study wether there is an association between the practice of
    sports and this type of cancer, a sample of 1000 males was drawn, of
    which 700 practiced sports, and it was observed that there were 2
    males with cancer in the group of males who practiced sports, and
    there were 3 males with cancer in the group of males who did not
    practice sports. Compute the relative risk and the odds ratio and
    interpret them.
  \end{enumerate}

  \textbf{Solution}\\
  Let \(D\) the event corresponding to suffering COVID19 and \(+\) and
  \(-\) the events corresponding to get a positive and a negative
  outcome respectively.

  \begin{enumerate}
  \item
    The sensitivity is \(P(+|D) = 0.58\) and specificity
    \(P(-|\overline D) = 0.01\).
  \item
    Positive predictive value \(P(D|+) = 0.0205\) and negative
    predictive value \(P(\overline D|-) = 0.4\). As de positive
    predictive value is less than 0.5 we can not use this test to
    confirm COVID19, but we can use it to rule it out with a strong
    confidence since the negative predictive value is pretty close to 1.
  \item
    \(P(D\cap +) + P(\overline D\cap -) = 0.0297\).
  \end{enumerate}
\item
  \textbf{Question}\\
  The probability that a child of a mother with the color-blind gene and
  a father without the color-blind gene is a color-blind male is
  \(0.25\). It is also known that in a population there is one
  color-blind male for every 5000 males.

  \begin{enumerate}
  \item
    If this couple has 5 children, what is the probability that at most
    2 of them are color-blind males?
  \item
    If this couple has 5 children, and the gender of the children is
    equiprobable, what is the probability that 3 or more are females?
  \item
    In a random samble of 10000 males of this population, what is the
    probability that more than 3 are color-blind males?
  \end{enumerate}

  \textbf{Solution}\\
\item
  \textbf{Question}\\
  The primate cranial capacity follows a normal distribution with mean
  1200 cm\(^3\) and standard deviation 140 cm\(^3\).

  \begin{enumerate}
  \item
    Compute the probability that the cranial capacity of a primate is
    greater than 1400 cm\(^3\).
  \item
    Compute the probability that the cranial capacity of a primate is
    exactly than 1400 cm\(^3\).
  \item
    Above what cranial capacity will 20\% of primates be?
  \item
    Compute the interquartile range of the cranial capacity of primates
    and interpret it.
  \end{enumerate}

  \textbf{Solution}\\
  Let \(X\) and \(Y\) be the prolactin levels in pregnant and
  non-pregnan females respectively.
\end{enumerate}
