\begin{enumerate}
\item
  \textbf{Question}\\
  Two symptoms of COVID-19 are fever and cough. We know that 30\% of
  people with COVID-19 cough and 20\% have fever and cough. Also, if
  somebody with COVID-19 have fever then the probability of coughing
  0.5.

  \begin{enumerate}
  \item
    Construct the probability tree for the sample space of the random
    experiment consisting in picking a random person with COVID-19 and
    measuring the symptoms that he or she have.
  \item
    Calculate the probability of having any of the symptoms.
  \item
    Calculate the probability of having only cough.
  \item
    Calculate the probability of having only fever.
  \item
    Calculate the probability no fever nor cough.
  \item
    Are the symptoms dependent or independent?
  \end{enumerate}

  \textbf{Solution}\\
  Let \(C\) and \(F\) be the events of having cough and fever
  respectively. According to the statement \(P(C)=0.3\),
  \(P(C\cap F)=0.2\) and \(P(C|F)=0.5\).

  \begin{enumerate}
  \item
    \(P(C\cup F) = 0.5\).
  \item
    \(P(C\cap \overline F) = 0.1\).
  \item
    \(P(\overline C \cap F) = 0.2\).
  \item
    \(P(\overline C \cap \overline F) = 0.5\).
  \item
    The events are dependent since \(P(C)\neq P(C|F)\).
  \end{enumerate}
\item
  \textbf{Question}\\
  The sensitivity and specificity of a diagnostic test are 0.58 and
  0.01, respectively, and the probability of a true positive is 0.02.

  \begin{enumerate}
  \item
    Calculate the prevalence of the disease.
  \item
    Calculate predictive values.
  \item
    Is the test more useful to rule out or confirm the disease?
  \item
    If we have 10 non-sick patients, what is the probability that more
    than 9 have a misdiagnosis?
  \item
    If we have 60 patients, what is the probability that at least two of
    them have a correct diagnosis?
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    \(P(D) = 0.0345\).
  \item
    \(PPV = P(D|+) = 0.0205\) and \(NPV = P(\overline D|-) = 0.4\).
  \item
    The test is not helpful to confirm nor to rule out the disease,
    since both the positive and the negative predictive values are below
    0.5.
  \item
    Let \(X\) be the number non sick patients with a positive outcome,
    then \(X\sim B(10, 0.99)\), and \(P(X\geq 9)=0.9957\).
  \item
    Let \(Y\) be the number of patients with a right diagnose, then
    \(Y\sim B(60, 0.0297)\approx P(1.7793)\), and \(P(Y\geq 2)=0.531\).
  \end{enumerate}
\item
  \textbf{Question}\\
  The time required to cure a basketball injury with a rehabilitation
  technique follows a normal distribution with quartiles \(Q_1 = 22\)
  days and \(Q_2 = 25\) days.

  \begin{enumerate}
  \item
    Calculate the mean and standard deviation of the curation time.
  \item
    If a player has just been injured and has to play a match in 30
    days, what is the probability that he will miss it?
  \item
    Calculate the interquartile range of the curation time distribution.
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    Let \(X\) be the time required to cure the injury, then
    \(X\sim N(25, 4.4478)\).
  \item
    \(P(X > 30) = 0.1305\).
  \item
    \(IQR = 6\) days.
  \end{enumerate}
\end{enumerate}
