\begin{enumerate}
\item
  \textbf{Question}\\
  The weight of male Wistar rats in a laboratory follows a normal
  distribution with mean 400 grams and standard deviation 30 grams.

  \begin{enumerate}
  \item
    What is the probability that a random rat weighs exactly 400 grams?
  \item
    What is the probability that a random rat weighs more than 450
    grams?
  \item
    If a rat is chosen randomly, what is the probability that its weight
    is an outlier?\\
    Remark: The normal range of data is \((Q_1-1.5 IQR, Q_3+1.5IQR)\).
  \item
    Give an interval of weights centered on the mean in which 95\% of
    the male Wistar rats are found.
  \end{enumerate}

  \textbf{Solution}\\
\item
  \textbf{Question}\\
  To evaluate a possible displacement of the patella at the Abruna Joms
  physiotherapy clinic, the Glide Test is used. After applying the test
  to 1000 patients we observed that 200 suffered from patella
  displacement and got a positive outcome, 13 suffered from patella
  displacement and got a negative outcome and 8 did not suffer patella
  displacement and got a positive outcome.

  \begin{enumerate}
  \item
    Represents the data obtained by the Glide test in a table or a tree.
  \item
    Compute the sensitivity and specificity of the Glide test.
  \item
    Is the Glide test useful for diagnosing patella displacement?
  \item
    Is the Glide test useful for ruling out patella displacement?
  \item
    What is the probability of getting a right diagnose?
  \end{enumerate}

  \textbf{Solution}\\
\item
  \textbf{Question}\\
  The new drug Recalnal for mitigating kidney stones produces side
  effects in the form of liver damage in 5\% of patients taking
  Recalnal. The drug is administered to 10 patients.

  \begin{enumerate}
  \item
    Justify the type of distribution followed by the variable that
    measures the number of patients with liver damage.
  \item
    What is the probability that at least 2 of them have liver damage?
  \item
    Let \(E_n\) be the event that at least one of \(n\) patients suffers
    liver damage when receiving Recalnal. In drug feasibility
    experiments \(P(E_n)\) is used as a criterion about how safe the
    drug is. What is the minimum value of \(n\) such that
    \(P(E_n)>0.9\)?
  \end{enumerate}

  In the experimental phase of Recalnal, an average of 3 doses per
  minute are administered to volunteers.

  \begin{enumerate}
  \item
    Justify the type of distribution followed by the variable that
    measures the number of doses administered every 5 minutes.
  \item
    What is the probability that 13 doses are administered in 5 minutes?
  \end{enumerate}

  \textbf{Solution}\\
\item
  \textbf{Question}\\
  In a population there are 20\% of patients who have suffered from
  disease \(A\) but not \(B\), 30\% of patients who have suffered from
  \(B\) but not \(A\), and 90\% of patients who have not suffered from
  both diseases (but may have suffered from one).

  \begin{enumerate}
  \item
    What percentage of people have suffered the disease \(A\)? And the
    disease \(B\)?
  \item
    Compute the probability of suffering some of the diseases.
  \item
    Calculate the probability of not suffering from disease \(B\) if
    disease \(A\) has not been suffered.
  \item
    What percentage of patients with disease \(B\) should there be in
    the population for both diseases to be independent?
  \end{enumerate}

  \textbf{Solution}\\
\end{enumerate}
