\begin{enumerate}
\item
  \textbf{Question}\\
  (2 pts.) In a population where the prevalence of a disease is 10\% we
  apply a diagnostic test with a sensitivity 85\%. What must be the
  minimum specificity of the test to diagnose the disease when the
  outcome of the test is positive?

  \textbf{Solution}\\
  The specificity must be at least \(0.9056\).
\item
  \textbf{Question}\\
  In a stretch of a road there is an average of 2 accidents per day.

  \begin{enumerate}
  \item
    Compute the probability of having more than 2 accidents a random
    day.
  \item
    Compute the probability of having more than 2 accidents a random
    day, knowing that there is at least one accident that day.
  \item
    Compute the probability of having 14 accidents a random week.
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    Let \(X\) be the number of accidents in a day. \(X\sim P(2)\) and
    \(P(X>2)=0.3233\).
  \item
    \(P(X>2|X\geq 1)=0.3739\).
  \item
    Let \(Y\) be the number of accidents in a week. \(X\sim P(14)\) and
    \(P(X=14)=0.106\).
  \end{enumerate}
\item
  \textbf{Question}\\
  In a study about the efectiveness of two flu drugs \(A\) and \(B\) it
  has been observed in a clinical trial that in 12\% of cases only drug
  \(A\) is effective, in 24\% of cases only drug \(B\) is effective and
  in 80\% of cases where drug \(A\) was effective, also was effective
  the drug \(B\).

  \begin{enumerate}
  \item
    What is the probability that both drugs are efective at the same
    time?
  \item
    What is the probability that only one of the drugs is effective?
  \item
    What is the probability that none of the drugs are effective?
  \item
    Are the effectiveness of the two drugs independent?
  \end{enumerate}

  \textbf{Solution}\\
  According to the problem statement, \(P(A\cap \overline B) = 0.12\),
  \(P(\overline A\cap B)=0.24\) and \(P(B|A)=0.8\).

  \begin{enumerate}
  \item
    \(P(A\cap B)=0.48\).
  \item
    \(P(A\cap \overline B) + P(\overline A\cap B) =0.36\).
  \item
    \(P(\overline A \cap \overline B) = 0.16\).
  \item
    The events are dependent because \(P(B)=0.72 \neq P(B|A)=0.8\).
  \end{enumerate}
\item
  \textbf{Question}\\
  It is known that the annual rainfall in a region follows a normal
  probability distribution. If the statistics show that 15\% of the
  years the annual rainfall has been greater than 45 cm and 3\% of the
  years less than 30 cm,

  \begin{enumerate}
  \item
    Compute the mean and the stantdard deviation of the annual
    rainfall.\\
    \textbf{Remark}: Use \(\mu=40\) cm y \(\sigma=3\) cm for the next
    part if you do not know how to compute them.
  \item
    What is the probability that in the next 5 years at least one year
    the annual rainfall was above 50 cm?
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    Let \(X\) be the annual rainfall. \(X\sim N(\mu, \sigma)\), and
    according to the statement \(P(X>45)=0.15\) and \(P(X<30)=0.03\).\\
    \(\mu=39.6708\) cm and \(\sigma=5.1419\) cm.
  \item
    Let \(Y\) be the number of years in the next 5 years with annual
    rainfall above 50 cm. Then \(Y\sim B(5, 0.0223)\), and
    \(P(X\geq 1)=0.1065\).
  \end{enumerate}
\end{enumerate}
