\begin{enumerate}
\item
  \textbf{Question}\\
  To study the association between the osteoporosis and the gender a
  random sample of people between 65 and 70 years old was taken. The
  following table summarize the results

  \[\begin{array}{lcc}
  \hline
  & \mbox{Osteoporosis} & \mbox{Not osteoporosis}\\
  \mbox{Women} & 480 & 2320\\
  \mbox{Men} & 255 & 1505\\
  \hline
  \end{array}\]

  \begin{enumerate}
  \item
    Compute the prevalence of the osteoporosis in the population.
  \item
    Compute the relative risk of osteoporosis in females with respect to
    males and interpret it.
  \item
    Compute the odds ratio of osteoporosis in females with respect to
    males and interpret it.
  \item
    Which of the two measures is most suitable to study the association
    between the osteoporosis and the gender?
  \end{enumerate}

  \textbf{Solution}\\
  Let \(D\) be the event of suffering osteoporosis.

  \begin{enumerate}
  \item
    Prevalence: \(P(D)=0.1612\).
  \item
    \(RR(D)=1.1832\). Thus, the risk of suffering osteoporosis in women
    is higher than in men but not to much. There is no strong
    association between the osteoporosis and the gender.
  \item
    \(OR(D)=1.2211\). Thus, the odds of suffering osteoporosis in women
    is higher than in men but not to much.
  \item
    Since we can compute the prevalence of \(D\), both statistics are
    suitable, but relative risk is easier to interpret.
  \end{enumerate}
\item
  \textbf{Question}\\
  The risks of getting the flu in two cities \(A\) and \(B\) with the
  same population size are 14\% and 8\% respectively.

  \begin{enumerate}
  \item
    Compute the probability of having more than 2 persons getting the
    flu in a random sample of 10 persons of the city \(A\).
  \item
    Compute the probability of having more than 2 and less than 5
    persons getting the flu in a random sample of 50 persons of the city
    \(B\).
  \item
    Compute the probability of having 2 persons getting the flu in a
    random sample of 8 persons of the two cities.
  \item
    Compute the probability of having some person getting the flu in a
    random sample of 5 persons that have been living in both cities.
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    Let \(X\) be the number of persons with flu in a sample of 10
    persons from \(A\), then \(X\sim B(10, 0.14)\) and
    \(P(X>2)=0.1545\).
  \item
    Let \(Y\) be the number of persons with flu in a sample of 50
    persons from \(B\), then \(Y\sim B(50, 0.08)\approx P(4)\) and
    \(P(2 < Y < 5) = 0.3907\).
  \item
    Let \(Z\) be the number of persons with flu in a sample of 8 persons
    from \(A\) and \(B\), then \(Z\sim B(8, 0.11)\) and
    \(P(Z = 2) = 0.1684\).
  \item
    Let \(U\) be the number of persons with flu in a sample of 5 persons
    living in both cities, then \(U\sim B(5, 0.2088)\) and
    \(P(U>0)=0.69\).
  \end{enumerate}
\item
  \textbf{Question}\\
  In a study about the cholesterol two samples of 10000 males and 10000
  females was taken. It was observed that 3420 males and 1234 females
  had a cholesterol level above 230 mg/dl, and that 4936 males had a
  cholesterol level between 210 and 230 mg/dl. Assuming that the
  cholesterol level in males and females follows a normal distribution
  with the same standard deviation, compute:

  \begin{enumerate}
  \item
    The means and the standard deviation of the distributions of
    cholesterol level in males and females.
  \item
    The percentage of males with cholesterol level between 200 and 240
    mg/dl.
  \item
    The interquartile range of the cholesterol level of females.
  \end{enumerate}

  \textbf{Solution}\\

  \begin{enumerate}
  \item
    Let \(X\) be cholesterol level in males and \(Y\) the cholesterol
    level in females, then \(X\sim N(224.1164, 14.4556)\) and
    \(X\sim N(213.2581, 14.4556)\)
  \item
    \(P(200\leq X \leq 240) = 0.8164\).
  \item
    \(IQR = 19.5003\) mg/dl.
  \end{enumerate}
\end{enumerate}
