
```{r echo=FALSE, results=hide}
## DATA GENERATION
require(xtable)
classes <- c("(10,14]", "(14,18]", "(18,22]", "(22,26]", "(26,30]")
xi <- xi <- seq(12, 28, by=4)
nxi <- c(6, 10, 7, 6, 1 )
x <- rep(xi, nxi)
data <- data.frame(classes, nxi)
colnames(data) <- c("Patients", "Frequency")

## QUESTION/ANSWER GENERATION
# sample size
nx <- length(x)
# quartiles
q1 <- quantile(x, probs = c(0.25), type=1)
q2 <- quantile(x, probs = c(0.5), type=1)
q3 <- quantile(x, probs = c(0.75), type=1)
# interquartile range
iqr <- q3-q1
#fences
f1 <- q1-1.5*iqr
f2 <- q3+1.5*iqr
# outliers
outliers <- x[x < f1 | x > f2]
# means
mx <- mean(x)
my <- 35
# variances
s2x <- sum(x^2)/nx-mx^2
s2y <- 40
# standard deviation
sx <- sqrt(s2x)
sy <- sqrt(s2y)
# coef. variation
cvx <- sx/mx
cvy <- sy/my
# coef. skewness
g1x <- sum((x-mx)^3)/(nx*sx^3)
# coef. kurtosis
g2x <- sum((x-mx)^4)/(nx*sx^4)-3
# standard scores
zx <- (20-mx)/sx
zy <- (40-my)/sy
```

Question
========
The table below shows the daily number of patients hospitalized in a hospital during the month of September.

```{r echo=FALSE}
print(xtable(data, align=c("c", "c", "r"), auto=T), tabular.environment="array", include.rownames = F, floating=F, hline.after = c(0,nrow(data)), sanitize.text.function = function(x) { x })
```

a. Study the spread of the 50%: of central data.
a. Compute the mean and study the dispersion with respect to it. 
a. Study the normality of the patients distribution.
a. If the mean was 35 patients and the variance 40 patients$^2$ during the month of April, which month had a higher relative variability?
a. Which number of people hospitalized was greater, 20 persons in September or 40 in April?


Use the following sums for the computations:  
$\sum x_in_i=`r sum(x)`$ patients, $\sum x_i^2n_i=`r sum(x^2)`$ patients$^2$, $\sum (x_i-\bar x)^3n_i=`r round(sum((x-mx)^3),2)`$ patients$^3$ and\\ $\sum (x_i-\bar x)^4n_i = `r round(sum((x-mx)^4),2)`$ patients$^4$.  

Solution
========
a. $Q_1=`r round(q1,4)`$ patients, $Q_3=`r round(q3,4)`$ patients and $IQR=`r round(iqr,4)`$ patients. Thus the central dispersion is small. 
a. $\bar x=`r round(mx,4)`$ patients, $s^2=`r round(s2x,4)`$ patients$^2$, $s=`r round(sx,4)`$ patients and $cv=`r round(cvx,4)`$. Thus, the dispersion with respect to the mean is small and the mean represents well.
a. $g_1=`r round(g1x,4)`$ and $g_2=`r round(g2x,4)`$. As the coefficient of skewness and the coefficient of kurtosis fall between -2 and 2, we can assume that the sample comes from a normal population.
a. Let $Y$ be the daily number of patients hospitalized during April. Then, $cv_y=`r round(cvy,4)`$. Since the coefficient of variation in April is greater than the one in September, there is a relative higher variability in April.
a. September: $z(20)=`r round(zx, 4)`$.  
April: $z(40)=`r round(zy, 4)`$.  
Thus, 40 patients hospitalized in April is relatively higher than 20 in September as its standard score is greater.

Meta-information 
================
extype: num
exsolution: Solution
exname: des-med-13
extol: 0.001
degree: Medicine
   
