
```{r echo=FALSE, results=hide}
## DATA GENERATION
library(kntir)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
x <- c(31, 32, 33, 33, 35, 35, 37, 37, 38, 39, 39, 41, 41, 42, 45, 46, 46, 47, 48, 48, 48, 52, 52, 54, 55, 55, 56, 57, 59, 61)
table <- matrix(c(x[1:15],x[16:30]), nrow = 2, byrow = T)
# QUESTION/ANSWER GENERATION
# Tamaño de la muestra
nx <- length(x)
# Media
mx <- mean(x)
# Mode
find_mode <- function(x) {
  u <- unique(x)
  tab <- tabulate(match(x, u))
  u[tab == max(tab)]
}
modex <- find_mode(x)
# Varianza
s2x <- sum(x^2)/nx-mx^2
# Desviación típica
sx <- sqrt(s2x)
# Coef. variación
cvx <- sx/mx
# Coef. asimetría
g1x <- sum((x-mx)^3)/(nx*sx^3)
# Coef. apuntamiento
g2x <- sum((x-mx)^4)/(nx*sx^4)-3
# Puntuaciones típicas
```

Question
========
The account of the pharmacist-tiktoker @farmaceutikofer has numerous informative-satirical videos on infectious diseases, sex education and healthy habits. The duration, in seconds, of his last 30 videos is as follows:

```{r echo=FALSE}
kable(data) %>% kable_styling()
```

a. Compute the average and the most frequent value of the duration of the videos.
a. How is the relative dispersion of the sample?
a. Construct the frequency table of the sample grouping the data into classes of amplitude 5 seconds and plot the histogram.
a. Compute the interquartile range and explains its meaning.
a. Has the distribution a normal kurtosis?
a. The ticktoker @pauloGsow uploads satirical videos about high school teachers with a mean duration of 45 seconds and a variance of 91 seconds. If both @farmaceutikofer and @pauloGsow upload a 51-second video, which of the two tiktokers has uploaded a shorter video in relation to their own account?


Use the following sums for the computations:  
$\sum x_i=`r sum(x)`$ s, $\sum x_i^2=`r sum(x^2)`$ s$^2$, $\sum (x_i-\bar x)^3=`r round(sum((x-mx)^3),2)`$ s$^3$ y $\sum (x_i-\bar x)^4=`r round(sum((x-mx)^4),2)`$  s$^4$.

Solution
========


Meta-information 
================
extype: num
exsolution: Solution
exname: des-22-med
extol: 0.001
%% \degree{Nutrition}
 
