
```{r echo=FALSE, results=hide}
## DATA GENERATION
require(xtable)
classes <- c("10-30", "30-45", "45-60", "60-90", "90-120", "120-180")
ni <- c(2, 11, 18, 9, 8, 2)
x <- rep(c(20, 37.5, 52.5, 75, 105, 150), ni)
data <- data.frame(classes, ni)
colnames(data) <- c("Time", "Patients")

## QUESTION/ANSWER GENERATION
# sample size
n <- length(x)
# cum rel frequencies
f <- cumsum(ni)/sum(ni)
# Quartiles 
q1 <- 30 + (0.25-f[1])/(f[2]-f[1])*(45-30)
q3 <- 60 + (0.75-f[3])/(f[4]-f[3])*(90-60)
# interquartile range
iqr <- q3-q1
#fences
f1 <- q1-1.5*iqr
f2 <- q3+1.5*iqr
# outliers
outliers <- x[x < f1 | x > f2]
# means
mx <- mean(x)
my <- 50
# variances
s2x <- sum(x^2)/n-mx^2
# standard deviation
sx <- sqrt(s2x)
sy <- 15
# coef. variation
cvx <- sx/mx
# Percentile 85
p85 <- 90 + (0.85-f[4])/(f[5]-f[4])*(120-90)
# coef. skewness
g1x <- sum((x-mx)^3)/(n*sx^3)
# coef. kurtosis
g2x <- sum((x-mx)^4)/(n*sx^4)-3
# standard scores
zx <- (70-mx)/sx
zy <- (60-my)/sy
```
  
Question
========
The table below summarizes the time (in minutes) required to remove anesthesia after a surgery in a sample of 50 patients.

```{r echo=FALSE}
kable(data) %>% kable_styling()
```
  
a. Are there some outliers in the sample?
a. Compute the mean. Is it representative?
a. If according to a postoperative protocol the 15%: of patients that require more time to remove the anesthesia must be monitored, above what time should a patient be monitored?
a. If we apply a drug that is anesthesia antagonist, it is known that the time required to remove the anesthesia decreases a 25%:. How will the time decrease affect the representativeness of the mean?
a. If it is known that another type of anesthesia $B$ has mean 50 minutes and standard deviation 15 minutes, what time is relatively greater, 70 minutes with this type of anesthesia or 60 minutes with the type $B$?.


Use the following sums for the computations: $\sum x_in_i=`r sum(x)`$ min, $\sum x_i^2n_i=`r sum(x^2)`$ min$^2$, $\sum (x_i-\bar x)^3n_i=`r round(sum((x-mx)^3),2)`$ min$^3$ y $\sum (x_i-\bar x)^4n_i=`r round(sum((x-mx)^4),2)`$ min$^4$.  

Solution
========
a. $Q_1=`r round(q1,4)`$, $Q_3=`r round(q3,4)`$, $IQR=`r round(iqr,4)`$, $f_1=`r round(f1,4)`$ and $f_2=`r round(f2,4)`$. Since the last class contains values above the upper fence, there could be outliers. 
a. $\bar x=`r round(mx,4)`$ min, $s^2=`r round(s2x,4)`$ min$^2$, $s=`r round(sx,4)`$ min and $cv=`r round(cvx,4)`$
Thus the representativity of the mean is moderate.
a. $P_{85}=`r round(p85,4)`$ min.
a. Applying the linear transformation $y=0.75x$, $\bar y=`r round(0.75*mx,4)`$ min, $s_y=`r round(0.75*sx,4)`$ min and $cv=`r round(cvx,4)`$.
Thus the representativity of the mean is the same.
a. Standard score in first anesthesia: $z(70)=`r round(zx,4)`$.  
Standard score in anesthesia $B$: $z(60)=`r round(zy,4)`$.  
Thus, 60 min with anesthesia $B$ is relatively greater.

Meta-information 
================
extype: num
exsolution: Solution
exname: des-gen-6
extol: 0.001
degree: Medicine

