
```{r echo=FALSE, results="hide"}
## DATA GENERATION
require(xtable)
classes <- c("0-1", "1-2", "2-3", "3-4", "4-5", "5-6", "6-7", "7-8")
xi <- seq(0.5, 7.5, 1)
nxi <- c(11, 18, 10, 8, 6, 4, 1, 2)
x <- rep(xi, nxi)
nyi <- c(5, 13, 6, 10, 9, 1, 0, 8)
y <- rep(xi, nyi)
data <- data.frame(classes, nxi, nyi)
colnames(data) <- c("Postoperative months", "Patients without suture", "Patients with suture")
## QUESTION/ANSWER GENERATION
# sample size
nx <- length(x)
ny <- length(y)
# quartiles
q1 <- 1.222
q2 <- quantile(x, probs = c(0.5), type=8)
q3 <- 3.7502
# interquartile range
iqr <- q3-q1
#fences
f1 <- q1-1.5*iqr
f2 <- q3+1.5*iqr
# outliers
outliers <- x[x < f1 | x > f2]
# means
mx <- mean(x)
my <- mean(y)
# variances
s2x <- sum(x^2)/nx-mx^2
s2y <- sum(y^2)/ny-my^2
# standard deviation
sx <- sqrt(s2x)
sy <- sqrt(s2y)
# coef. variation
cvx <- sx/mx
cvy <- sy/my
# coef. skewness
g1x <- sum((x-mx)^3)/(nx*sx^3)
g1y <- sum((y-my)^3)/(ny*sy^3)
# coef. kurtosis
g2x <- sum((x-mx)^4)/(nx*sx^4)-3
g2y <- sum((y-my)^4)/(ny*sy^4)-3
# standard scores
zx <- (5-mx)/sx
zy <- (6-my)/sy
```

Question
========
In a study on the reconstruction of the anterior cruciate ligament (ACL), the postoperative recovery time was evaluated depending on whether the patients underwent a meniscal suture or not. The table below contains the results:

```{r echo=FALSE}
print(xtable(data, align=c("c", "c", "r", "r"), auto=T), tabular.environment="array", include.rownames = F, floating=F, hline.after = c(0,nrow(data)), sanitize.text.function = function(x) { x })
```


a. Plot the ogive for the sample of patients without meniscal suture.

a. Are there outliers in the number of postoperative moths of patients without meniscal suture?

a. In which of the two groups is more representative the mean of the postoperative months?

a. Can we assume that the sample of patients with meniscal suture comes from a normal population?

a. What value is relatively greater, 5 months for a patient without meniscal suture, or 6 for a patient with meniscal suture?


Use the following sums for the computations:  
Without meniscal suture: $\sum x_in_i=`r sum(x)`$ months, $\sum x_i^2n_i=`r sum(x^2)`$ months$^2$, $\sum (x_i-\bar x)^3n_i=`r round(sum((x-mx)^3),2)`$ months$^3$ y $\sum (x_i-\bar x)^4n_i=`r round(sum((x-mx)^4),2)`$ months$^4$.  
With meniscal suture: $\sum y_in_i=`r sum(y)`$ months, $\sum y_i^2n_i=`r sum(y^2)`$ months$^2$, $\sum (y_i-\bar y)^3n_i=`r round(sum((y-my)^3),2)`$ months$^3$ y $\sum (y_i-\bar y)^4n_i=`r round(sum((y-my)^4),2)`$ months$^4$.

Solution
========

a. 
```{r cumulative-frequencies-polygon, fig=T, echo=F, height=3, width=4, dev="svg", fig.path="img"}
library(ggplot2)
u <- seq(0, 8)
v <- cumsum(c(0, nxi)) / nx
data <- data.frame(u, v)
p <- ggplot(data, aes(x=u, y=v)) + 
  geom_line(color='steelblue') + xlab("Postoperatory months") + 
  ylab("Cumulative relative frequency") +
  scale_x_continuous(breaks = 0:8) +
  scale_y_continuous(breaks = 0:10/10) +
  theme(plot.title = element_text(hjust = 0.5), axis.title=element_text(size=10))
print(p)
```

a. $Q_1=`r round(q1,4)`$ months, $Q_3=`r round(q3,4)`$ months, $IQR=`r round(iqr,4)`$ month, $f_1=`r round(f1,4)`$ and $f_2=`r round(f2,4)`$. Since the upper limit of the last interval is greater than the upper fence, there could be outliers in the sample.

a. Without suture: $\bar x=`r round(mx,4)`$ months, $s^2=`r round(s2x,4)`$ months$^2$, $s=`r round(sx,4)`$ months and $cv=`r round(cvx,4)`$.  
With suture: $\bar y=`r round(my,4)`$ months, $s^2=`r round(s2y,4)`$ months$^2$, $s=`r round(sy,4)`$ months and $cv=`r round(cvy,4)`$.  
Thus, the mean of the sample with suture is more representative since its coefficient of variation is smaller.

a. $g_1=`r round(g1y,4)`$ and $g_2=`r round(g2y,4)`$. Since both coefficients are between -2 and 2, we can assume that the sample comes from a normal population.

a. Without suture: $z(5)=`r round(zx,4)`$.  
With suture: $z(6)=`r round(zy,4)`$.  
Thus, 5 months in the sample without suture is relatively greater, since its standard score is greater.

Meta-information 
================
extype: num
exsolution: Solution
exname: des-fis-8
extol: 0.001
%% \degree{Physioterapy}
 
