
```{r echo=FALSE, results="hide"}
## DATA GENERATION
library(knitr)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(tidyverse)
library(kableExtra)
df <- tibble(
    `Failed subjects` = c(0, 1, 2, 3, 4, 5, 6, 8), 
    `Previous year course` = c(7, 15, 11, 5, 4, 2, 1, 0), 
    `Current course` = c(8, 12, 8, 7, 3, 2, 2, 1))
# QUESTION/ANSWER GENERATION
x <- rep(df$`Failed subjects`, df$`Previous year course`)
y <- rep(df$`Failed subjects`, df$`Current course`)
# Tamaño de la muestra
nx <- length(x)
ny <- length(y)
# Media
mx <- mean(x)
my <- mean(y)
# Varianza
s2x <- sum(x^2)/nx-mx^2
s2y <- sum(y^2)/ny-my^2
# Desviación típica
sx <- sqrt(s2x)
sy <- sqrt(s2y)
# Coef. variación
cvx <- sx/mx
cvy <- sy/my
# Coef. asimetría
g1x <- sum((x-mx)^3)/(nx*sx^3)
g1y <- sum((y-my)^3)/(ny*sy^3)
# Coef. apuntamiento
g2x <- sum((x-mx)^4)/(nx*sx^4)-3
g2y <- sum((y-my)^4)/(ny*sy^4)-3
# Puntuaciones típicas
zx <- (6-mx)/sx
zy <- (7-my)/sy
```

Question
========
To see if the confinement due to COVID-19 influenced the performance of a course, the number of failed subjects of each student in the current course and in the previous year course has been counted, obtaining the table below.

```{r echo=FALSE}
kable(df) %>% kable_styling()
```

a.  Draw the box plots of the failed subjects in the current and the previous year courses and compare them.

a.  Can we assume that both samples come from a normal population?

a.  In which sample is the mean more representative?

a.  Which number of failed subjects is relatively greater, 7 in the current course or 6 in the previous year course?


Use the following sums for the computations:  
Previous year course: $\sum x_i=`r sum(x)`$ subjects, $\sum x_i^2=`r sum(x^2)`$ subjects$^2$, $\sum (x_i-\bar x)^3=`r round(sum((x-mx)^3),2)`$ subjects$^3$ y $\sum (x_i-\bar x)^4=`r round(sum((x-mx)^4),2)`$  subjects$^4$.  
Current course: $\sum x_i=`r sum(y)`$ subjects, $\sum x_i^2=`r sum(y^2)`$ subjects$^2$, $\sum (x_i-\bar x)^3=`r round(sum((y-my)^3),2)`$ subjects$^3$ y $\sum (x_i-\bar x)^4=`r round(sum((y-my)^4),2)`$  subjects$^4$.  

Solution
========
a.  Box plot

```{r box-plot}
tibble(Course = c(rep("Previous year course", nx), rep("Current course", ny)), `Failed subjects` = c(x, y))  %>%  
    ggplot(aes(x = Course, y = `Failed subjects`)) +
    geom_boxplot()
```

a.  Previous year course: $\bar x = `r round(mx, 4)`$ subjects, $s_x^2=`r round(s2x,4)`$ subjects$^2$, $s_x=`r round(sx,4)`$ subjects, $g_1 = `r round(g1x,4)`$ and $g_2 = `r round(g2x,4)`$.  
Current course: $\bar x = `r round(my, 4)`$ subjects, $s_x^2=`r round(s2y,4)`$ subjects$^2$, $s_x=`r round(sy,4)`$ subjects, $g_1 = `r round(g1y,4)`$ and $g_2 = `r round(g2y,4)`$.  
In both courses the coefficients of skewness and kurtosis are between -2 and 2, so we can assume that both samples come from a normal population.

a.  Previous year course: $cv = `r round(cvx, 4)`$.  
Current year course: $cv = `r round(cvy, 4)`$.  
As the coefficient of variation of the previous year course is smaller, its mean is a little bit more representative.

a.  Previous year course: $z(6) = `r round(zx, 4)`$.  
Current course: $z(7) = `r round(zy, 4)`$.  
Thus, 6 failed subjects is relative greater in the previous year course than 7 failed subjects in the current course.

Meta-information 
================
extype: string
exsolution: Solution
exname: des-26-gen
extol: 0.001
degree: All
 
