
```{r echo=FALSE, results=hide}
## DATA GENERATION
library(kntir)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
x <- c(175, 182, 190, 165, 172, 183, 187, 174, 168, 178)
y <- c(164, 175, 165, 160, 155, 172, 160, 151, 165, 163)
z <- c(177, 180, 193, 172, 173, 188, 185, 177, 168, 182)
data <- data.frame(x, y, z)
colnames(data) <- c("Father's height", "Mother's height", "Son's height")
n <- length(x)

## QUESTION/ANSWER GENERATION
# Sample size
nx <- length(x)
ny <- length(y)
nz <- length(z)
# Quartiles
q1 <- quantile(z, probs = c(0.25), type=1)
q2 <- quantile(z, probs = c(0.5), type=1)
q3 <- quantile(z, probs = c(0.75), type=1)
# IQR
iqr <- q3-q1
# Fences
f1 <- q1-1.5*iqr
f2 <- q3+1.5*iqr
# Outliers
outliers <- z[z < f1 | z > f2]
# Mean
mx <- mean(x)
my <- mean(y)
mz <- mean(z)
# Varianza
s2x <- sum(x^2)/nx-mx^2
s2y <- sum(y^2)/ny-my^2
s2z <- sum(z^2)/nz-mz^2
# St.deviation
sx <- sqrt(s2x)
sy <- sqrt(s2y)
sz <- sqrt(s2z)
# Coef. variation
cvx <- sx/mx
cvy <- sy/my
cvz <- sz/mz
# Coef. skewness
g1x <- sum((x-mx)^3)/(nx*sx^3)
g1y <- sum((y-my)^3)/(ny*sy^3)
g1z <- sum((z-mz)^3)/(nz*sz^3)
# Coef. kurtosis
g2x <- sum((x-mx)^4)/(nx*sx^4)-3
g2y <- sum((y-my)^4)/(ny*sy^4)-3
g2z <- sum((z-mz)^4)/(nz*sz^4)-3
# Standard scores
zy <- (165-my)/sy
zz <- (178-mz)/sz
```

Question
========
In a sample of 10 families with a son older than 20 it has been measured the height of the father ($X$), the mother ($Y$) and the son ($Z$) in centimetres, getting the following results: 

```{r echo=FALSE}
kable(data) %>% kable_styling()
```

a. In which sample is the mean more representative, in the sample of fathers or mothers?
a. Are there outliers in the sample of sons? 
a. According to the shape of the distribution, can the sample of mothers come from a normal population?
a. Who is higher in her/his sample, a mother 165 cm tall or a son 178 cm tall?
a. If we had measured the heights in meters, how the representativity of the mean would have been affected?



Use the following sums for the computations:  
Father's height: $\sum x_i=`r sum(x)`$ cm, $\sum x_i^2=`r sum(x^2)`$ cm$^2$, $\sum (x_i-\bar x)^3=`r round(sum((x-mx)^3),2)`$ cm$^3$ y $\sum (x_i-\bar x)^4=`r round(sum((x-mx)^4),2)`$ cm$^4$.  
Mother's height: $\sum y_i=`r sum(y)`$ cm, $\sum y_i^2=`r sum(y^2)`$ cm$^2$, $\sum (y_i-\bar y)^3=`r round(sum((y-my)^3),2)`$ cm$^3$ y $\sum (y_i-\bar y)^4=`r round(sum((y-my)^4),2)`$ cm$^4$.   
Son's height: $\sum z_i=`r sum(z)`$ cm, $\sum z_i^2=`r sum(z^2)`$ cm$^2$, $\sum (z_i-\bar z)^3=`r round(sum((z-mz)^3),2)`$ cm$^3$ y $\sum (z_i-\bar z)^4=`r round(sum((z-mz)^4),2)`$ cm$^4$.

Solution
========
a. Padres: $\bar x=`r round(mx,4)`$ cm, $s^2=`r round(s2x,4)`$ cm$^2$, $s=`r round(sx,4)`$ cm y $cv=`r round(cvx,4)`$.  
Madres: $\bar y=`r round(my,4)`$ cm, $s^2=`r round(s2y,4)`$ cm$^2$, $s=`r round(sy,4)`$ cm y $cv=`r round(cvy,4)`$.  
La estatura media es un poco más representativa en el grupo de las madres.
a. Las vallas en la muestra de hijos son $f_1=`r round(f1,2)`$ cm y $f_2=`r round(f2,2)`$ cm por lo que no hay estaturas atípicas entre los hijos.
a. $g_{1y}=`r round(g1y,4)`$ y $g_{2y}=`r round(g2y,4)`$. Como el coeficiente de asimetría y el de apuntamiento están dentro del intervalo de -2 a 2, podemos asumir que la muestra de estaturas de madres proviene de una población normal.
a.  Puntuación típica madres: $z(165)=`r round(zy, 4)`$.  
Puntuación típica hijos: $z(178)=`r round(zz, 4)`$.  
Así pues, una madre de 165 cm es relativamente más alta que un hijo de 178 cm.
a. La respresentatividad de las medias no cambiaría ya que tanto las medias como las desviaciones típicas estarían divididas por 100.

Meta-information 
================
extype: num
exsolution: Solution
exname: des-gen-15
extol: 0.001
degree: Optics
 
