
```{r echo=FALSE, results=hide}
## DATA GENERATION
require(xtable)
classes <- c("(30,35]", "(35,40]", "(40,45]", "(45,50]")
xi <- c(32.5, 37.5, 42.5, 47.5)
ni <- c(15, 35, 40, 10)
x <- rep(xi,ni)
data <- data.frame(classes, ni)
colnames(data) <- c("Time (min)", "Num runners")
## QUESTION/ANSWER GENERATION
# sample size
nx <- length(x)
# quartiles
q1 <- 36.4286
q3 <- 43.125
# interquartile range
iqr <- q3-q1
#fences
f1 <- q1-1.5*iqr
f2 <- q3+1.5*iqr
# outliers
outliers <- x[x < f1 | x > f2]
# means
mx <- mean(x)
my <- 40
# variances
s2x <- sum(x^2)/nx-mx^2
# standard deviation
sx <- sqrt(s2x)
sy <- 5
# coef. variation
cvx <- sx/mx
cvy <- sy/my
# coef. skewness
g1x <- sum((x-mx)^3)/(nx*sx^3)
g1y <- 0.75
# standard scores
zx <- (39-mx)/sx
zy <- (39-my)/sy
```

Question
========
The table below summarize the time that took to the runners to reach the finish in a long-distance race in Madrid: 

```{r echo=FALSE}
kable(data) %>% kable_styling()
```

In a another race in Paris, the mean of time was 40 minutes, the standard deviation 5 minutes and the coeffitient of skewness $0.75$.

a. What percentage of runners took less than 42 minutes to reach the finish in Madrid?
a. Compute and interpret the interquartile range of the time for Madrid race.
a. In which race the mean of the time is more representative?
a. In which race the time have a more simmetric distribution?
a. In which race a time of 39 minutes to reach the finish is relatively smaller?


Use the following sums for the computations: $\sum x_i=`r sum(x)`$ min, $\sum x_i^2=`r sum(x^2)`$ min$^2$, $\sum (x_i-\bar x)^3=`r round(sum((x-mx)^3),2)`$ min$^3$ y $\sum (x_i-\bar x)^4=`r round(sum((x-mx)^4),2)`$ min$^4$.

Solution
========
a. $F(42)=0.66$, thus approximately $66%:$ of runners finished before 42 minutes.
a. $Q_1=`r round(q1,4)`$ min, $Q_3=`r round(q3,4)`$ min, $IQR=`r round(iqr,4)`$ min. The central 50%: of times fall in a range of $`r round(iqr,4)`$ minutes.
a. Madrid statistics: $\bar x=`r round(mx,4)`$ min, $s^2=`r round(s2x,4)`$ min$^2$, $s=`r round(sx,4)`$ min and $cv=`r round(cvx,4)`$.  
Paris statistics: $cv=`r round(cvy,4)`$. Thus, the mean of time in Madrid is a little bit more representative since the coef. of variation is smaller.
a. $g_1=`r round(g1x,4)`$, that is closer to 0 than the distribution of times in Paris, thus the distribution of times in Madrid is more simmetric.
a. The standard score of the Madrid sample is $z(39)=`r round(zx,4)`$ and the standard score of the Paris one $z(39)=`r round(zy,4)`$, thus a time of 39 min is relatively smaller in the sample of Paris.

Meta-information 
================
extype: num
exsolution: Solution
exname: des-far-2
extol: 0.001
degree: Pharmacy
 
