
```{r echo=FALSE, results="hide"}
## DATA GENERATION
library(knitr)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
x <- c(4.7, 3.6, 5.2, 6.8, 9.5, 4.8, 5.6, 5.4)
y <- c(3.2, 4.5, 5.4, 2.1, 6.7, 5.2, 3.8, 4.3, 7.2, 2.6)
data <- matrix(c(x, NA, NA, y), ncol=10, byrow=T)
rownames(data) <- c("Men ($X$)", "Women ($Y$)")
n <- length(y)

## QUESTION/ANSWER GENERATION
# Tamaño de la muestra
nx <- length(x)
ny <- length(y)
# Media
mx <- mean(x)
my <- mean(y)
# Varianza
s2x <- sum(x^2)/nx-mx^2
s2y <- sum(y^2)/ny-my^2
# Desviación típica
sx <- sqrt(s2x)
sy <- sqrt(s2y)
# Coef. variación
cvx <- sx/mx
cvy <- sy/my
# Coef. asimetría
g1x <- sum((x-mx)^3)/(nx*sx^3)
g1y <- sum((y-my)^3)/(ny*sy^3)
# Coef. apuntamiento
g2x <- sum((x-mx)^4)/(nx*sx^4)-3
g2y <- sum((y-my)^4)/(ny*sy^4)-3
# Puntuaciones típicas
zx <- (6-mx)/sx
vy <- my + zx * sy
```

Question
========
The table below shows the blood uric acid concentration of 8 men and 10 women in mg/dl.

```{r echo=FALSE}
kable(data) %>% kable_styling()
```

Se pide: 


a. In which group, men or women, is the mean more representative?

a. In which group, men or women, is the uric acid distribucion more simmetric?

a. In which group, men or women, is the uric acid distribution flatter?

a. Can we assume that the uric acid sample from women comes from a normal population?

a. What uric acid concentration must a woman have to be relative higher than 6 mg/dl in a man?

a. If all the values of the variable $X$ are multiplied by a number, what must that number be to make the mean of the new variable as representative as the mean of $Y$?


Use the following sums for the computations:  
Men: $\sum x_i=`r sum(x)`$ mg/dl, $\sum x_i^2=`r sum(x^2)`$ (mg/dl)$^2$, $\sum (x_i-\bar x)^3=`r round(sum((x-mx)^3),2)`$ (mg/dl)$^3$ and $\sum (x_i-\bar x)^4=`r round(sum((x-mx)^4),2)`$ (mg/dl)$^4$.  
Women: $\sum y_i=`r sum(y)`$ mg/dl, $\sum y_i^2=`r sum(y^2)`$ (mg/dl)$^2$, $\sum (y_i-\bar y)^3=`r round(sum((y-my)^3),2)`$ (mg/dl)$^3$ and $\sum (y_i-\bar y)^4=`r round(sum((y-my)^4),2)`$ (mg/dl)$^4$.   

Solution
========

a. Men: $\bar x=`r round(mx,4)`$ mg/dl, $s^2=`r round(s2x,4)`$ (mg/dl)$^2$, $s=`r round(sx,4)`$ mg/dl and $cv=`r round(cvx,4)`$.  
Women: $\bar y=`r round(my,4)`$ mg/dl, $s^2=`r round(s2y,4)`$ (mg/dl)$^2$, $s=`r round(sy,4)`$ mg/dl and $cv=`r round(cvy,4)`$.  
Thus, the mean of uric acid is more representative in men than in women as the coefficient of variation is smaller.   

a. $g_{1x}=`r round(g1x,4)`$ and $g_{1y}=`r round(g1y,4)`$. Thus, the distribution of uric acid in men is more symmetric as the coefficient of skewness is closer to 0.

a. $g_{2x}=`r round(g2x,4)`$ and $g_{2y}=`r round(g2y,4)`$. Thus, the distribution of uric acid in men is flatter as the coefficient of kurtosis is smaller.

a. As the coefficient of skewness and the coefficient of kurtosis are between -2 and 2 we can assume that the uric acid sample of women comes from a normal population.

a. The uric acid must be at least $`r round(vy,4)`$.

Meta-information 
================
extype: num
exsolution: Solution
exname: des-med-17
extol: 0.001
degree: Medicine
 
