```{r data generation, echo=FALSE, results="hide"}
## DATA GENERATION
set.seed(123)
x <- rep(c(4.5, 5.5, 6.5, 7.5, 8.5), c(2, 5, 6, 4, 3))
y <- rep(c(2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5), c(1, 6, 7, 3, 7, 0, 1))
data <- data.frame(Score = c(x, y), Treatment = c(rep('Treatment', 20), rep('Placebo', 25)))

## QUESTION/ANSWER GENERATION
# Tamaño de la muestra
nx <- length(x)
ny <- length(y)
# Quartiles
q1 <- quantile(y, probs = c(0.25), type=1)
q2 <- quantile(y, probs = c(0.5), type=1)
q3 <- quantile(y, probs = c(0.75), type=1)
# IQR
iqr <- q3-q1
# Fences
f1 <- q1-1.5*iqr
f2 <- q3+1.5*iqr
# Outliers
outliers <- y[y < f1 | y > f2]
# Mean
mx <- mean(x)
my <- mean(y)
# Variance
s2x <- sum(x^2)/nx-mx^2
s2y <- sum(y^2)/ny-my^2
# Std. deviation
sx <- sqrt(s2x)
sy <- sqrt(s2y)
# Coef. variation
cvx <- sx/mx
cvy <- sy/my
# Coef. skewness
g1x <- sum((x-mx)^3)/(nx*sx^3)
g1y <- sum((y-my)^3)/(ny*sy^3)
# Coef. kurtosis
g2x <- sum((x-mx)^4)/(nx*sx^4)-3
g2y <- sum((y-my)^4)/(ny*sy^4)-3
# Standard scores
zx <- (5-mx)/sx
zy <- (6-my)/sy
```

Question
========

\puntos{5}To study the effectiveness of a new treatment for the polymyalgia rheumatica a sample of patients with polymyalgia was drawn and they were divided into two groups. The first group received the new treatment while the second one received a placebo. After a year following the treatment they filled out a survey. The chart below shows the distribution of the survey score of the two groups of patients (the greater the score the better the treatment).

```{r}
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
```


```{r back-back-scores-distribution, fig=T, echo=F, dev="png", fig.path="img"}
# Histogram by sex
library(Hmisc)
options(digits=1)
blueceulight <- rgb(137, 211, 243, 255, maxColorValue = 255) #89D3F3
orangeceu <- rgb(248, 131, 121, 255, maxColorValue = 255)#F88379
out <- histbackback(split(data$Score, data$Treatment), xlim=c(-8,8), main = 'Frequency distribution of scores', axes = F)
axis(side = 1, at = -8:8, labels = c(8:0,1:8))
axis(side = 2, at = seq(0, 7, 1), labels = 2:9)
mtext("Score", side = 2, line = 3, cex = par("cex.lab"))
mtext("Placebo                              Treatment", side = 1, line = 3, cex = par("cex.lab"))
abline(v= (-8:8)*2 , col ="gray" , lty =3) 
barplot(-out$left, col=blueceulight , horiz = T, space = 0, add = T, axes = F) 
barplot(out$right, col=orangeceu, horiz = T, space = 0, add = T, axes = F) 
```

1. Construct the frequency table of the scores for the placebo group and plot the ogive.
2. Compute the interquartile range of the scores for the placebo group.
3. Are there outliers in the placebo group?
4. In which group the score mean represents better?
5. Which distribution is more normal regarding the kurtosis?
6. Which score is relatively better, a score of 5 in the placebo group or a score of 6 in the treatment group?

Use the following sums for the computations: \\
Treatment: $\sum x_i=`r round(sum(x), 2)`$.


Solution
========


META-INFORMATION
================
extype: num
exsolution: Solution
exname: des-18-gen
exto: 0.001
degree: All
 
