
```{r echo=FALSE, results="hide"}
## DATA GENERATION
require(xtable)
classes <- c("0-2", "2-4", "4-6", "6-8", "8-10")
xi <- c(1, 3, 5, 7, 9)
nxi <- c(8, 15, 25, 38, 14)
x <- rep(xi, nxi)
nyi <- c(2, 9, 19, 11, 9)
y <- rep(xi, nyi)
data <- data.frame(classes, nxi, nyi)
colnames(data) <- c("Grade", "Num non-working students", "Num working students")
## QUESTION/ANSWER GENERATION
# sample size
nx <- length(x)
ny <- length(y)
# quartiles
q1 <- quantile(x, probs = c(0.25), type=1)
q2 <- quantile(x, probs = c(0.5), type=1)
q3 <- quantile(x, probs = c(0.75), type=1)
# interquartile range
iqr <- q3-q1
#fences
f1 <- q1-1.5*iqr
f2 <- q3+1.5*iqr
# outliers
outliers <- x[x < f1 | x > f2]
# means
mx <- mean(x)
my <- mean(y)
# variances
s2x <- sum(x^2)/nx-mx^2
s2y <- sum(y^2)/ny-my^2
# standard deviation
sx <- sqrt(s2x)
sy <- sqrt(s2y)
# coef. variation
cvx <- sx/mx
cvy <- sy/my
# coef. skewness
g1x <- sum((x-mx)^3)/(nx*sx^3)
g1y <- sum((y-my)^3)/(ny*sy^3)
# Transformación lineal
myx <- 0.5 + mx * 1.45
myy <- 0.5 + my * 1.45
# standard scores
zx <- (7-mx)/sx
zy <- (6-my)/sy
```

Question
========
In a course there are 150 students, of which 50 are working students and the other 100 non-working students. The table below shows the frequency distribution of the grade in an exam of these two groups:

```{r echo=FALSE}
print(xtable(data, align=c("c", "c", "r", "r"), auto=T), tabular.environment="array", include.rownames = F, floating=F, hline.after = c(0,nrow(data)), sanitize.text.function = function(x) { x })
```


a. Compute the percentage of students that passed the exam (a grade 5 or above) in both groups, working and non-working students.

a. In which group is there a higher relative dispersion of the grade with respect to the mean? 

a. Which grade distribution is more asymmetric, the distribution of working students, or the non-working students one?

a. To apply for a scholarship to go abroad, the grade must be transformed applying the linear transformation Y = 0.5 + X * 1.45. Compute the mean of Y for the two groups. How changes the asymmetry of the two groups?

a. Which grade is relatively higher, 6 in the working students group, or 7 in the non-working students group?


Use the following sums for the computations:  
Non-working students: $\sum x_in_i=`r sum(x)`$, $\sum x_i^2n_i=`r sum(x^2)`$, $\sum (x_i-\bar x)^3n_i=`r round(sum((x-mx)^3),2)`$ y $\sum (x_i-\bar x)^4n_i=`r round(sum((x-mx)^4),2)`$.  
Working students: $\sum y_in_i=`r sum(y)`$, $\sum y_i^2n_i=`r sum(y^2)`$, $\sum (y_i-\bar y)^3n_i=`r round(sum((y-my)^3),2)`$ y $\sum (y_i-\bar y)^4n_i=`r round(sum((y-my)^4),2)`$.

Solution
========

a. 66.5% of non-working stsudents passed and 59% of working students passed.

a. Non-working students: $\bar x=`r round(mx,4)`$, $s^2=`r round(s2x,4)`$, $s=`r round(sx,4)`$ and $cv=`r round(cvx,4)`$.  
Working students: $\bar y=`r round(my,4)`$, $s^2=`r round(s2y,4)`$, $s=`r round(sy,4)`$ and $cv=`r round(cvy,4)`$.  
The sample of non-working students has a slightly higher relative dispersion with respect to the mean as the coefficient of variation is greater.

a. Non-working students: $g_1=`r round(g1x,4)`$.  
Working students: $g_1=`r round(g1y,4)`$.  
Thus, the sample of non-working students is more assymetric as the coefficient os skewness is further from 0.

a. Non-working students: $\bar y=`r round(myx, 4)`$.  
Working students: $\bar x=`r round(myy, 4)`$.  
The coefficient of skewness does not change as the slope of the linear transformation is positive.  

a. Non-working students: $z(7)=`r round(zx, 4)`$.  
Working students: $z(6)=`r round(zy, 4)`$.  
Thus, a 7 in the sample of non-working students is relatively higher than than a 6 in the sample of working students, as its standard score is greater.

Meta-information 
================
extype: num
exsolution: Solution
exname: des-fis-11
extol: 0.001
degree: All
   
