
```{r echo=FALSE, results="hide"}
## DATA GENERATION
library(knitr)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
#library(rkTeaching)  // I get an error in the compilation
x <- c(rep(0,12),rep(1,36),rep(2,39),rep(3,24), rep(4, 6), rep(5, 3))
df <- data.frame(Drinks = x)

## QUESTION/ANSWER GENERATION
# Sample size
nx <- length(x)
# Quartiles
q1 <- quantile(x, 0.25, type = 1)
q2 <- quantile(x, 0.5, type = 1)
q3 <- quantile(x, 0.75, type = 1)
# IQR
iqr <- q3-q1
# Fences
f1 <- q1-1.5*iqr
f2 <- q3+1.5*iqr
# Outliers
outliers <- x[x < f1 | x > f2]
# Mean
mx <- mean(x)
my <- 2.1
# Variance
s2x <- sum(x^2)/nx-mx^2
s2y <- 1.5
# Std. deviation
sx <- sqrt(s2x)
sy <- sqrt(s2y)
# Coef. variation
cvx <- sx/mx
cvy <- sy/my
# Coef. skewness
g1x <- sum((x-mx)^3)/(nx*sx^3)
# Coef. kurtosis
g2x <- sum((x-mx)^4)/(nx*sx^4)-3
# Standard scores
zx <- (3 - mx) / sx
zy <- (4 - my) / sy
```

Question
========
The table below shows the number of daily sugary drinks drunk by a sample of 16-years-old people.

$$
\begin{array}{|c|r|r|r|r|}
\hline
\mbox{Drinks} & n_i & f_i & N_i & F_i\\
\hline
0 &    & 0.1 &     &      \\
\hline
1 &    &     & 48  &      \\
\hline
2 &    &     &     & 0.725\\
\hline
3 & 24 &     &     &      \\
\hline
4 &    &     &     & 0.975\\
\hline
5 &    &     & 120 &      \\
\hline
\end{array}
$$


a. Complete the table explaining how.

a. Plot the cumulative frequency polygon.

a. Are there outliers?

a. Study the normality of the distribution.

a. If another sample of 18-years-old people has a mean $2.1$ drinks and a variance $1.5$ drinks$^2$, in which distribution is more representative the mean?

a. Who consumes a higher relative amount of sugary drinks, a 16-years-old who consumes 3 drinks a day or a 18-years-old who consumes 4?

Use the following sums for the computations: $\sum x_i= `r sum(x)`$ drinks, $\sum x_i^2=`r sum(x^2)`$ drinks$^2$, $\sum (x_i-\bar x)^3=`r round(sum((x-mx)^3),2)`$ drinks$^3$ and $\sum (x_i-\bar x)^4=`r round(sum((x-mx)^4),2)`$ drinks$^4$.

Solution
========

a. 
```{r echo = F, comment = NA}
table <- rkTeaching::frequencyTable(df, "Drinks")
print(xtable(table, auto=T), tabular.environment="array", include.rownames = F,  floating=F, hline.after = c(0,nrow(table)), sanitize.text.function = function(x) { x })
```

a. 
```{r cumulative-distribution-subjects, fig=T, echo=F, height=4, width=6, dev="svg", fig.path="img"}
Ni <- cumsum(table(x))
xi <- c(-0.5, rep(sort(unique(x)), each=2), 5.5)
Ni <- c(0, 0, rep(Ni, each=2))
plot(xi, Ni, type="l", col="blue",
     main = "Distribution of daily sugary drinks",
     xlab = "Num of drinks",
     ylab = "Cumulative frequency")
abline(h=seq(0,120,20), col = "gray", lty=2)
lines(xi, Ni, col="blue")
```

a. Quartiles: $Q_1=`r q1`$ drinks, $Q_2=`r q2`$ drinks, $Q_3=`r q3`$ drinks  
$IQR = `r iqr`$ drinks  
Fences: $f_1=`r f1`$ drinks and $f_2=`r f2`$ drinks.

a. $\bar x=`r round(mx,4)`$ drinks, $s^2=`r round(s2x,4)`$ drinks$^2$, $s=`r round(sx,4)`$ drinks, 
$g_1=`r round(g1x,4)`$ and $g_2=`r round(g2x,4)`$. As the coefficient of skewness and the coefficient of kurtosis are between -2 and 2 we can assume that the sample comes from a normal population.

a. Let $Y$ be the daily sugary drinks drunk by 18-year-old people. Then, $cv_x=`r round(cvx,4)`$ and $cv_y=`r round(cvy,4)`$. As the coefficient of variation of 18-year-old is a little bit smaller than the one of 16-year-old, the mean of the 18-year-old is a little bit more representative.

a. Standard score for 16-year-old: $z(3)=`r round(zx, 4)`$  
Standard score for 18-year-old: $z(4)=`r round(zy, 4)`$  
As the standard score of 4 for a 18-year-old is greater than the standard score of 3 for a 16-years-old, 4 drinks is relatively higher.

Meta-information 
================
extype: num
exsolution: Solution
exname: des-21-nut
extol: 0.001
%% \degree{Nutrition}
 
