
```{r echo=FALSE, results=hide}
## DATA GENERATION
require(xtable)
classes <- c("(0,5]", "(5,10]", "(10,15]", "(15,20]", "(20,30]", "(30,60]")
xi <- c(2.5, 7.5, 12.5, 17.5, 25, 45)
ni <- c(5, 15, 32, 36, 42, 20)
x <- rep(xi,ni)
data <- data.frame(classes, ni)
colnames(data) <- c("Response time", "Patients")
## QUESTION/ANSWER GENERATION
# sample size
n <- length(x)
# cum rel frequencies
f <- cumsum(ni)/sum(ni)
# Q1
q1 <- 10 + (0.25-f[2])/(f[3]-f[2])*(15-10)
q3 <- 20 + (0.75-f[4])/(f[5]-f[4])*(30-20)
p80 <- 20 + (0.8-f[4])/(f[5]-f[4])*(30-20)
# interquartile range
iqr <- q3-q1
#fences
f1 <- q1-1.5*iqr
f2 <- q3+1.5*iqr
# outliers
outliers <- x[x < f1 | x > f2]
# means
m <- mean(x)
# variances
s2 <- sum(x^2)/n-m^2
# standard deviation
s <- sqrt(s2)
# coef. variation
cv <- s/m
# coef. skewness
g1 <- sum((x-m)^3)/(n*s^3)
# coef. kurtosis
g2 <- sum((x-m)^4)/(n*s^4)-3
# standard scores
z1 <- (25-m)/s
z2 <- (25-18)/15
```

Question
========
The time required by a drug $A$ to be effective has been measured (in minutes) in a sample of 150 patients.
The table below summarize the results.

```{r echo=FALSE}
kable(data) %>% kable_styling()
```

a. Are there outliers in the sample?
Justify the answer.
a. What is the minimum time for the 20%: of patients with highest response time?
a. What is the average response time?
Is the mean representative?
a. Can we assume that the sample comes from a normal population?
a. If we take another sample of patients with mean 18 min and standard deviation 15 min, in which group is greater a response time of 25 min?

Use the following sums for the computations: $\sum x_in_i=`r sum(x)`$ min, $\sum x_i^2n_i=`r sum(x^2)`$ min$^2$, $\sum (x_i-\bar x)^3n_i=`r round(sum((x-m)^3),2)`$ min$^3$ y $\sum (x_i-\bar x)^4n_i=`r round(sum((x-m)^4),2)`$ min$^4$.

Solution
========
a. $Q_1=`r round(q1,4)`$ min, $Q_3=`r round(q3,4)`$ min, $IQR=`r round(iqr,4)`$ min, $f_1=`r round(f1,4)`$ min and $f_2=`r round(f2,4)`$ min. Therefore there are outliers in the sample since the upper limit of the last interval is above the upper fence.
a. $P_{80}=`r round(p80,4)`$ min.
a. $\bar x=`r round(m,4)`$ min, $s^2=`r round(s2,4)`$ min$^2$, $s=`r round(s,4)`$ min and $cv=`r round(cv,4)`$.
The mean is not very representative since the $cv>0.5$. 
a. $g_1=`r round(g1,4)`$ and $g_2=`r round(g2,4)`$. Since $g_1$ and $g_2$ are between -2 and 2, we can assumme that the sample comes from a normal (bell-shaped) population.
a. The standard score of the first sample is $z(25)=`r round(z1,4)`$ and the standard score of the second one $z(25)=`r round(z2,4)`$, thus a time of 25 min is relatively greater in the second sample.

Meta-information 
================
extype: num
exsolution: Solution
exname: des-far-2
extol: 0.001
degree: Pharmacy
 
