
```{r echo=FALSE, results=hide}
## DATA GENERATION
require(xtable)
xi <- c(0, 1, 2, 3, 4, 5, 6, 8)
nxi <- c(7, 15, 11, 5, 4, 2, 1, 0)
x <- rep(xi, nxi)
nyi <- c(8, 12, 8, 7, 3, 2, 2, 1)
y <- rep(xi, nyi)
data <- data.frame(xi, nxi, nyi)
colnames(data) <- c("Failed subjects", "Previous year course", "Current course")
## QUESTION/ANSWER GENERATION
# sample size
nx <- length(x)
ny <- length(y)
# quartiles
q1 <- quantile(x, probs = c(0.25), type=1)
q2 <- quantile(x, probs = c(0.5), type=1)
q3 <- quantile(x, probs = c(0.75), type=1)
# interquartile range
iqr <- q3-q1
#fences
f1 <- q1-1.5*iqr
f2 <- q3+1.5*iqr
# outliers
outliers <- x[x < f1 | x > f2]
# means
mx <- mean(x)
my <- mean(y)
# variances
s2x <- sum(x^2)/nx-mx^2
s2y <- sum(y^2)/ny-my^2
# standard deviation
sx <- sqrt(s2x)
sy <- sqrt(s2y)
# coef. variation
cvx <- sx/mx
cvy <- sy/my
# coef. skewness
g1x <- sum((x-mx)^3)/(nx*sx^3)
g1y <- sum((y-my)^3)/(ny*sy^3)
# coef. kurtosis
g2x <- sum((x-mx)^4)/(nx*sx^4)-3
g2y <- sum((y-my)^4)/(ny*sy^4)-3
# Transformación lineal
myx <- 0.5 + mx * 1.45
myy <- 0.5 + my * 1.45
# standard scores
zx <- (6-mx)/sx
zy <- (7-my)/sy
```

Question
========
	
To see if the confinement due to COVID-19 has influenced the performance of a course, the number of failed subjects of each student in the current course and in the previous year course has been counted, obtaining the table below.

```{r echo=FALSE}
print(xtable(data, align=c("c", "c", "r", "r"), auto=T), tabular.environment="array", include.rownames = F, floating=F, hline.after = c(0,nrow(data)), sanitize.text.function = function(x) { x })
```

Se pide:
a. Draw the box plots of the failed subjects in the current and the previous year courses and compare them.
a. Can we assume that both samples come from a normal population?
a. In which sample the mean is more representative?
a. Which number of failed subjects is greater, 7 in the current course or 6 in the previous year course?


Use the following sums for the computations:  
Previous year course: $\sum x_in_i=`r sum(x)`$, $\sum x_i^2n_i=`r sum(x^2)`$, $\sum (x_i-\bar x)^3n_i=`r round(sum((x-mx)^3),2)`$ y $\sum (x_i-\bar x)^4n_i=`r round(sum((x-mx)^4),2)`$.  
Current course: $\sum y_in_i=`r sum(y)`$, $\sum y_i^2n_i=`r sum(y^2)`$, $\sum (y_i-\bar y)^3n_i=`r round(sum((y-my)^3),2)`$ y $\sum (y_i-\bar y)^4n_i=`r round(sum((y-my)^4),2)`$.

Solution
========
a. 
```{r box-plot-scores, fig=T, echo=F, height=3, width=4, dev="svg", fig.path="img"}
library(ggplot2)
failed = c(x, y)
course = rep(c("Previous year course", "Current course"), c(nx, ny))
data <- data.frame(failed, course)
p <- ggplot(data, aes(x = failed, y = course, col = course)) + 
  geom_boxplot() + 
  labs(title = "Box plot of failed subjects", x = "Failed subjects", y = "") +
  theme(plot.title = element_text(hjust = 0.5), axis.title=element_text(size=10), legend.position = "none")
print(p)
```

Both distributions are pretty similar. The central dispersion is the same and both are right skewed. The only difference is that there is an outlier in the current year distribution.  
a. Previous year course: $\bar x=`r round(mx,4)`$, $s^2=`r round(s2x,4)`$, $s=`r round(sx,4)`$, $g_1=`r round(g1x,4)`$ and $g_2=`r round(g2x,4)`$.\\ 
Current course: $\bar y=`r round(my,4)`$, $s^2=`r round(s2y,4)`$, $s=`r round(sy,4)`$, $g_1=`r round(g1y,4)`$ and $g_2=`r round(g2y,4)`$.  
As the coefficients of skewness and kurtosis are between -2 and 2, we can assume that both distributions come from a normal distribution.
a. Previous year course: $cv=`r round(cvx,4)`$.  
Current year: $cv=`r round(cvy,4)`$.  
Thus, the mean is more representative in the previous year course, since the coefficient of variation is smaller.
a. Previous year course: $z(6)=`r round(zx, 4)`$.  
Current course: $z(7)=`r round(zy, 4)`$.  
Thus, 7 failed subjects in the current course is relatively less than 6 in the previous year course, since the standard score is smaller.

Meta-information 
================
extype: num
exsolution: Solution
exname: des-gen-12
extol: 0.001
degree: All
   
