
```{r echo=FALSE, results=hide}
## DATA GENERATION
library(kntir)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
x <- c(0.2, 0.7, 1, 1.5, 2, 2.4, 2.8, 3)
y <- c(40, 32, 28, 20, 18, 15, 12, 11)
table <- matrix(c(x,y), nrow = 2, byrow = T)
decimals <- matrix(c(rep(1,9), rep(0,9)), nrow = 2, ncol=9, byrow=TRUE)
rownames(table) <- c("Dose ($\\mu$g)", "Bacteria")
## QUESTION/ANSWER GENERATION
# colors  
col1 <- "#05A1E6"
# sample size
n <- length(x)
# means
mx <- mean(x)
mlogx <- mean(log(x))
my <- mean(y)
mlogy <- mean(log(y))
# variances
s2x <- sum(x^2)/n-mx^2
s2logx <- sum(log(x)^2)/n-mlogx^2
s2y <- sum(y^2)/n-my^2
s2logy <- sum(log(y)^2)/n-mlogy^2
# Covariances
sxy <- sum(x * y) / n - mx * my
sxlogy <- sum(x*log(y))/n-mx*mlogy
slogxy <- sum(log(x)*y)/n-mlogx*my
# Determination coeff
r2xy <-  sxy^2 / (s2x * s2y)
r2xlogy <- sxlogy^2/(s2x*s2logy)
r2logxy <- slogxy^2/(s2logx*s2y)
# Linear regression model
reglin <- lm(y ~ x)
# Exponential regression model y on x
regexp <- lm(log(y)~x)
# Logarithmic regression model x on y
reglog <- lm(y~log(x))
```

Question
========
\puntos{5 } 	
We have applied different doses of an antibiotic to a culture of bacteria. The table below shows the number of residual bacteria corresponding to the different doses.
```{r echo=FALSE}
kable(table) %>% kable_styling()
```

a. Which regression model explains better the number of residual bacteria as a function of the antibiotic dose, the linear or the exponential?
a. Use the best of the two previous regression models to predict the number of residual bacteria for an antibiotic dose of 3.5 $\mu$g. Is this prediction reliable?
a. According to the linear regression model, what is the expected decrease in the number of residual bacteria per each $\mu$g more of antibiotic?
Use the following sums for the computations ($X$=Antibiotic dose and $Y$=Number of bacteria):  
$\sum x_i=`r round(sum(x), 4)`$ $\mu$g, $\sum \log(x_i)=`r round(sum(log(x)), 4)`$ $\log(\mbox{$\mu$g})$, $\sum y_j=`r round(sum(y), 4)`$ bacteria, $\sum \log(y_j)=`r round(sum(log(y)), 4)`$ $\log(\mbox{bacteria})$,  
$\sum x_i^2=`r round(sum(x^2), 4)`$ $\mu$g$^2$, $\sum \log(x_i)^2=`r round(sum(log(x)^2), 4)`$ $\log(\mbox{$\mu$g})^2$, $\sum y_j^2=`r round(sum(y^2), 4)`$ bacteria$^2$, $\sum \log(y_j)^2=`r round(sum(log(y)^2), 4)`$ $\log(\mbox{bacteria})^2$,  
$\sum x_iy_j=`r round(sum(x*y), 4)`$ $\mu$g$\cdot$bacteria, $\sum x_i\log(y_j)=`r round(sum(x*log(y)), 4)`$ $\mu$g$\cdot\log(\mbox{bacteria})$, $\sum \log(x_i)y_j=`r round(sum(log(x)*y), 4)`$ $\log(\mbox{$\mu$g})$bacteria, $\sum \log(x_i)\log(y_j)=`r round(sum(log(x)*log(y)), 4)`$ $\log(\mbox{$\mu$g})\log(\mbox{bacteria})$.

Solution
========
a. $\overline{x}=`r round(mx,4)`$ $\mu$g, $s_x^2=`r round(s2x,4)`$ $\mu$g$^2$.  
$\bar y=`r round(my,4)`$ bacteria, $s_y^2=`r round(s2y,4)`$ bacteria$^2$.  
$s_{xy}=`r round(sxy,4)`$ $\mu$g$\cdot$bacteria.  
Linear coefficient of determination $r^2 = `r round(r2xy, 4)`$.  
$\overline{\log(y)}=`r round(mlogy,4)`$ log(bacteria), $s_{\log(y)}^2=`r round(s2logy,4)`$ log(bacteria)$^2$.  
$s_{x\log(y)}=`r round(sxlogy,4)`$ $\mu$g$\cdot$ log(bacteria).  
Exponential coefficient of determination $r^2 = `r round(r2xlogy, 4)`$.  
Thus, the exponential model explains better the number of residual bacteria as a function of the antibiotic dose because the exponential coef. of determination is greater.
a. Exponential regression model: $y=e^{`r round(regexp$coefficients[1],4)`+`r round(regexp$coefficients[2],4)`x}$.  
Prediction: $y(3.5)=`r round(exp(regexp$coefficients[1] + regexp$coefficients[2]*3.5),4)`$ bacteria.  
Although the coef. of determination is close to 1, the this prediction is not reliable because the sample size is very small.
a. $b_{yx}=`r round(reglin$coefficients[2], 4)`$, therefore the number of bacteria decreases $`r round(reglin$coefficients[2], 4)`$ per each $\mu$g more of antibiotic.

Meta-information 
================
extype: num
exsolution: Solution
exname: regnol-11-med
extol: 0.001
degree: Medicine
 
