
```{r echo=FALSE, results=hide}
## DATA GENERATION
library(kntir)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
x <- c(9, 10, 11, 12, 13, 14, 15, 16, 17, 18)
y <- c(128, 144, 148, 154, 158, 161, 165, 164, 166, 167)
table <- matrix(c(x,y), nrow = 2, byrow = T)
rownames(table) <- c("Age (years)", "Height (cm)")
## QUESTION/ANSWER GENERATION
# colors
col1 <- "#05A1E6"
# sample size
n <- length(x)
# means
mx <- mean(x)
mlogx <- mean(log(x))
my <- mean(y)
mlogy <- mean(log(y))
# variances
s2x <- sum(x^2)/n-mx^2
s2logx <- sum(log(x)^2)/n-mlogx^2
s2y <- sum(y^2)/n-my^2
s2logy <- sum(log(y)^2)/n-mlogy^2
# Covariances
sxy <- sum(x*y)/n-mx*my
slogxy <- sum(log(x)*y)/n-mlogx*my
# Deteryearsation coeff
r2xy <- sxy^2/(s2x*s2y)
r2logxy <- slogxy^2/(s2logx*s2y)
# Exponential regression model
regexp <- lm(log(y)~x)
# Logarithmic regression model
reglog <- lm(y~log(x))
```

Question
========
In a tennis club the age ($X$) and the height ($Y$) of the ten players conforming the female youth team has been measured.

```{r echo=FALSE}
kable(table) %>% kable_styling()
```

a. Plot the scatter plot (Height on Age).
a. Which regression model bests fits these data, the linear or the logarithmic?
a. What is the expected height of a player 12.5 years old according to the best of two previous models?


Use the following sums for the computations:  
$\sum x_i=`r round(sum(x), 4)`$ years, $\sum \log(x_i)=`r round(sum(log(x)), 4)`$ $\log(\mbox{years})$, $\sum y_j=`r round(sum(y), 4)`$ cm, $\sum \log(y_j)=`r round(sum(log(y)), 4)`$ $\log(\mbox{cm})$,  
$\sum x_i^2=`r round(sum(x^2), 4)`$ years$^2$, $\sum \log(x_i)^2=`r round(sum(log(x)^2), 4)`$ $\log(\mbox{years})^2$, $\sum y_j^2=`r round(sum(y^2), 4)`$ cm$^2$, $\sum \log(y_j)^2=`r round(sum(log(y)^2), 4)`$ $\log(\mbox{cm})^2$,  
$\sum x_iy_j=`r round(sum(x*y), 4)`$ years$\cdot$cm, $\sum x_i\log(y_j)=`r round(sum(x*log(y)), 4)`$ years$\cdot\log(\mbox{cm})$, $\sum \log(x_i)y_j=`r round(sum(log(x)*y), 4)`$ $\log(\mbox{years})$cm, $\sum \log(x_i)\log(y_j)=`r round(sum(log(x)*log(y)), 4)`$ $\log(\mbox{years})\log(\mbox{cm})$.

Solution
========
a. 
```{r scatterlot-height-age, fig=T, echo=F, dev="svg", fig.path="img"}
plot(x, y, main="Scatterplot of Height and Age", xlab="Age", ylab="Height", col=col1, pch=16)
```
a. $\bar x=`r round(mx,4)`$ years, $s_x^2=`r round(s2x,4)`$ years$^2$.  
$\overline{\log(x)}=`r round(mlogx,4)`$ log(years), $s_{\log(x)}^2=`r round(s2logx,4)`$ log(years)$^2$.  
$\bar y=`r round(my,4)`$ cm, $s_y^2=`r round(s2y,4)`$ cm$^2$.  
$s_{xy}=`r round(sxy,4)`$ years$\cdot$cm, $s_{\log(x)y}=`r round(slogxy,4)`$ log(years)cm  
Linear coef. determination: $r^2=`r round(r2xy,4)`$  
Logarithmic coef. determination: $r^2=`r round(r2logxy,4)`$  
Therefore, both models fit pretty well, but the logarithmic model fits a little bit better.
a. Logarithmic regression model: $y=`r round(reglog$coefficients[1],4)`+`r round(reglog$coefficients[2],4)`\log(x)$.  
Prediction: $y(12.5)=`r round(reglog$coefficients[1]+reglog$coefficients[2]*log(12.5), 4)`$ cm.

Meta-information 
================
extype: num
exsolution: Solution
exname: regnol-fis-4
extol: 0.001
degree: Physiotherapy
 
