
```{r echo=FALSE, results="hide"}
## DATA GENERATION
library(knitr)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
x <- c(5, 8, 20, 35, 50, 80, 110)
y <- c(50, 70, 100, 150, 170, 190, 200)
table <- matrix(c(x,y), nrow = 2, byrow = T)
#decimals <- matrix(c(rep(0,6), rep(2,6)), nrow = 3, ncol=6, byrow=TRUE)
rownames(table) <- c("Concentration ($\\mu$g/ml)", "Signal (Hz)")
## QUESTION/ANSWER GENERATION
# colors  
col1 <- "#05A1E6"
# sample size
n <- length(x)
# means
mx <- mean(x)
mlogx <- mean(log(x))
my <- mean(y)
mlogy <- mean(log(y))
# variances
s2x <- sum(x^2)/n-mx^2
s2logx <- sum(log(x)^2)/n-mlogx^2
s2y <- sum(y^2)/n-my^2
s2logy <- sum(log(y)^2)/n-mlogy^2
# Covariances
sxy <- sum(x * y) / n - mx * my
sxlogy <- sum(x*log(y))/n-mx*mlogy
slogxy <- sum(log(x)*y)/n-mlogx*my
# Determination coeff
r2xy <-  sxy^2 / (s2x * s2y)
r2xlogy <- sxlogy^2/(s2x*s2logy)
r2logxy <- slogxy^2/(s2logx*s2y)
# Linear regression model
reglin <- lm(y ~ x)
# Exponential regression model y on x
regexp <- lm(log(x)~y)
# Logarithmic regression model x on y
reglog <- lm(y~log(x))
```

Question
========
A study tries to develop a new technique for detecting a certain antibody. For this, a piezoelectric immunosensor is used, which allows to measure the change in the signal in Hz by varying the concentration of the antibody ($\mu$g/ml). The table below presents the data collected.

```{r echo=FALSE}
kable(table) %>% kable_styling()
```

Se pide:

a. Compute the logarithmic model of the change in the signal on the concentration of the antibodies.

a. It was observed that at a concentration of 100 $\mu$g/ml the change in signal tends to stabilize. Predict the value of the signal corresponding to such concentration using the logarithmic model.

a. Predict the antibody concentration that corresponds to a change in the signal of 120 using the exponential model.

Use the following sums for the computations ($X$=Concentration and $Y$=Signal):  
$\sum x_i=`r round(sum(x), 4)`$ Hz, $\sum \log(x_i)=`r round(sum(log(x)), 4)`$ $\log(\mbox{Hz})$, $\sum y_j=`r round(sum(y), 4)`$ $\mu$g/ml, $\sum \log(y_j)=`r round(sum(log(y)), 4)`$ $\log(\mbox{$\mu$g/ml})$,  
$\sum x_i^2=`r round(sum(x^2), 4)`$ Hz$^2$, $\sum \log(x_i)^2=`r round(sum(log(x)^2), 4)`$ $\log(\mbox{Hz})^2$, $\sum y_j^2=`r round(sum(y^2), 4)`$ $\mu$g/ml$^2$, $\sum \log(y_j)^2=`r round(sum(log(y)^2), 4)`$ $\log(\mbox{$\mu$g/ml})^2$,  
$\sum x_iy_j=`r round(sum(x*y), 4)`$ Hz$\cdot$$\mu$g/ml, $\sum x_i\log(y_j)=`r round(sum(x*log(y)), 4)`$ Hz$\cdot\log(\mbox{$\mu$g/ml})$, $\sum \log(x_i)y_j=`r round(sum(log(x)*y), 4)`$ $\log(\mbox{Hz})$$\mu$g/ml, $\sum \log(x_i)\log(y_j)=`r round(sum(log(x)*log(y)), 4)`$ $\log(\mbox{Hz})\log(\mbox{$\mu$g/ml})$.

Solution
========

a. $\overline{\log(x)}=`r round(mlogx,4)`$ log($\mu$g/ml), $s_{\log(x)}^2=`r round(s2logx,4)`$ log($\mu$g/ml)$^2$.  
$\bar y=`r round(my,4)`$ Hz, $s_y^2=`r round(s2y,4)`$ Hz$^2$.  
$s_{\log(x)y}=`r round(slogxy,4)`$ log($\mu$g/ml)Hz.  
Logarithmic regression model: $y=`r round(reglog$coefficients[1],4)`+`r round(reglog$coefficients[2],4)`\log(x)$.

a. Prediction: $y(100)=`r round(reglog$coefficients[1] + reglog$coefficients[2]*log(100),4)`$ Hz.

a. Exponential regression model: $y=e^{`r round(regexp$coefficients[1],4)`+`r round(regexp$coefficients[2],4)`y}$.  
Prediction: $y(120)=`r round(exp(regexp$coefficients[1] + regexp$coefficients[2]*120),4)`$ $\mu$g/ml.  

Meta-information 
================
extype: num
exsolution: Solution
exname: regnol-med-9
extol: 0.001
degree: Medicine
 
