
```{r echo=FALSE, results=hide}
## DATA GENERATION
library(kntir)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
set.seed(123)
x <- c(15, 35, 22, 28, 21, 18, 25, 30, 23, 20)
y <- round(exp(-0.15*x+6) + rnorm(length(x)))
table <- matrix(c(x,y), nrow = 2, byrow = T)
rownames(table) <- c("Warm-up time", "Injuries")
## QUESTION/ANSWER GENERATION
# sample size
n <- length(x)
# means
mx <- mean(x)
mlogx <- mean(log(x))
my <- mean(y)
mlogy <- mean(log(y))
# variances
s2x <- sum(x^2)/n-mx^2
s2logx <- sum(log(x)^2)/n-mlogx^2
s2y <- sum(y^2)/n-my^2
s2logy <- sum(log(y)^2)/n-mlogy^2
# Covariances
sxlogy <- sum(x*log(y))/n-mx*mlogy
slogxy <- sum(log(x)*y)/n-mlogx*my
# Determination coeff
r2xlogy <- sxlogy^2/(s2x*s2logy)
r2logxy <- slogxy^2/(s2logx*s2y)
# Exponential regression model
regexp <- lm(log(y)~x)
# Logarithmic regression model
reglog <- lm(y~log(x))
```

Question
========
The table below shows the number of injuries of several teams during a league and the average varm-up time of its players. 

```{r echo=FALSE}
kable(table) %>% kable_styling()
```

a. Draw the scatter plot.
a. Which regression model is more suitable to predict the number of injuries as a function of the warm-up time, the logarithmic or the exponential? 
Use that regression model to predict the expected number of injuries for a team whose players warm-up 20 minutes a day.
a. Which regression model is more suitable to predict the warm-up time as a function of the number of injuries, the logarithmic or the exponential? 
Use that regression model to predict the warm-up time required to have no more than 10 injuries in a league.
a. Are these predictions reliable? Which one is more reliable?

Use the following sums for the computations ($X$ warm-up time and $Y$ number of injuries):  
$\sum x_i=`r sum(x)`$, $\sum \log(x_i)=`r round(sum(log(x)),4)`$, $\sum y_j=`r sum(y)`$, $\sum \log(y_j)=`r round(sum(log(y)),4)`$,  
$\sum x_i^2=`r sum(x^2)`$, $\sum \log(x_i)^2=`r round(sum(log(x)^2),4)`$, $\sum y_j^2=`r sum(y^2)`$, $\sum \log(y_j)^2=`r round(sum(log(y)^2),4)`$,  
$\sum x_iy_j=`r sum(x*y)`$, $\sum x_i\log(y_j)=`r round(sum(x*log(y)),4)`$, $\sum \log(x_i)y_j=`r round(sum(log(x)*y),4)`$, $\sum \log(x_i)\log(y_j)=`r round(sum(log(x)*log(y)),4)`$.

Solution
========
a. 
```{r scatterplot-injuries-warm-up, fig=T, echo=F, height=4, width=5, dev=svg, fig.path="img"}
plot(x, y, main="Scatter plot of warm-up time and injuries", xlab = "Warm-up time", ylab="Injuries")
```
a. $\bar x=`r round(mx,4)`$ min, $s_x^2=`r round(s2x,4)`$ min$^2$.  
$\bar \log(x)=`r round(mlogx,4)`$ log(min), $s_{\log(x)}^2=`r round(s2logx,4)`$ log(min)$^2$.  
$\bar y=`r round(my,4)`$ injuries, $s_y^2=`r round(s2y,4)`$ injuries$^2$.  
$\bar \log(y)=`r round(mlogy,4)`$ log(injuries), $s_{\log(y)}^2=`r round(s2logy,4)`$ log(injuries)$^2$.  
$s_{x\log(y)}=`r round(sxlogy,4)`$, $s_{\log(x)y}=`r round(slogxy,4)`$  
Exponential determination coefficient: $r^2=`r round(r2xlogy,4)`$  
Logarithmic determination coefficient: $r^2=`r round(r2logxy,4)`$  
So the exponential regression model es better to predict the number of injuries as a function of the warm-up time.  
Exponential regression model: $y=e^{`r round(regexp$coefficients[1],4)`+`r round(regexp$coefficients[2],4)`x}$.  
Prediction: $y(20)=`r round(exp(regexp$coefficients[1] + regexp$coefficients[2]*20),4)`$ injuries.
a. The logarithmic model is better to predict the warm-up time as a function of the number or injuries.  
Logarithmic regression model: $x=`r round(reglog$coefficients[1],4)`+`r round(reglog$coefficients[2],4)`\log(y)$.  
Prediction: $x(10)=`r round(reglog$coefficients[1]+reglog$coefficients[2]*log(10),4)`$ min.
a. Both predictions are very reliable since de deternation coefficient is very high but the last one is a little less reliable as it is for a value further from the data range.

Meta-information 
================
extype: num
exsolution: Solution
exname: regnol-fis-1
extol: 0.001
degree: Physiotherapy
 
