
```{r echo=FALSE, results="hide"}
## DATA GENERATION
library(knitr)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
x <- c(4, 8, 12, 16, 20, 24)
y <- c(25.4, 24, 22.8, 22, 21.6, 21.4)
table <- matrix(c(x,y), nrow = 2, byrow = T)
rownames(table) <- c("Time of exercise", "BMI")
## QUESTION/ANSWER GENERATION
# sample size
n <- length(x)
# means
mx <- mean(x)
mlogx <- mean(log(x))
my <- mean(y)
mlogy <- mean(log(y))
# variances
s2x <- sum(x^2)/n-mx^2
s2logx <- sum(log(x)^2)/n-mlogx^2
s2y <- sum(y^2)/n-my^2
s2logy <- sum(log(y)^2)/n-mlogy^2
# Covariances
sxy <- sum(x*y)/n-mx*my
sxlogy <- sum(x*log(y))/n-mx*mlogy
slogxy <- sum(log(x)*y)/n-mlogx*my
# Linera model
reglin <- lm(y~x)
# Exponential regression model
regexp <- lm(log(y)~x)
# Logarithmic regression model
reglog <- lm(y~log(x))
# Determination coeff
r2xy <- sxy^2/(s2x*s2y)
r2xlogy <- sxlogy^2/(s2x*s2logy)
r2logxy <- slogxy^2/(s2logx*s2y)
```

Question
========
A person followed a program of exercises to reduce its body mass index (BMI).
The table below shows the BMI at different number of weeks doing exercise.

```{r echo=FALSE}
kable(table) %>% kable_styling()
```


a. Compute the BMI after 30 weeks doing exercise  using the linear, logarithmic and exponential regression models.

a. Which prediction is more reliable? Justify the answer.

Use the following sums for the computations ($X$ time of exercise and $Y$ BMI):  
$\sum x_i=`r sum(x)`$, $\sum \log(x_i)=`r round(sum(log(x)),4)`$, $\sum y_j=`r sum(y)`$, $\sum \log(y_j)=`r round(sum(log(y)),4)`$,  
$\sum x_i^2=`r sum(x^2)`$, $\sum \log(x_i)^2=`r round(sum(log(x)^2),4)`$, $\sum y_j^2=`r sum(y^2)`$, $\sum \log(y_j)^2=`r round(sum(log(y)^2),4)`$,  
$\sum x_iy_j=`r sum(x*y)`$, $\sum x_i\log(y_j)=`r round(sum(x*log(y)),4)`$, $\sum \log(x_i)y_j=`r round(sum(log(x)*y),4)`$, $\sum \log(x_i)\log(y_j)=`r round(sum(log(x)*log(y)),4)`$.

Solution
========

a. $\bar x=`r round(mx,4)`$ min, $s_x^2=`r round(s2x,4)`$ min$^2$.  
$\overline{\log(x)}=`r round(mlogx,4)`$ log(min), $s_{\log(x)}^2=`r round(s2logx,4)`$ log(min)$^2$.  
$\bar y=`r round(my,4)`$ kg/m$^2$, $s_y^2=`r round(s2y,4)`$ (kg/m$^2$)$^2$.  
$\overline{\log(y)}=`r round(mlogy,4)`$ log(kg/m$^2$), $s_{\log(y)}^2=`r round(s2logy,4)`$ log(kg/m$^2$)$^2$.  
$s_{xy}=`r round(sxy,4)`$ min$\cdot$kg/m$^2$, $s_{x\log(y)}=`r round(sxlogy,4)`$ log(min)kg/m$^2$, $s_{\log(x)y}=`r round(slogxy,4)`$ min$\cdot$log(kg/m$^2$)  
Linear regression model: $y=`r round(reglin$coefficients[1],4)`+`r round(reglin$coefficients[2],4)`x$.
Predicción: $y(30)=`r round(reglin$coefficients[1] + reglin$coefficients[2]*30,4)`$ kg/m$^2$.  
Logarithmic regression model: $y=`r round(reglog$coefficients[1],4)`+`r round(reglog$coefficients[2],4)`\log(x)$.
Predicción: $y(30)=`r round(reglog$coefficients[1] + reglog$coefficients[2]*log(30),4)`$ kg/m$^2$.  
Exponential regression model: $y=e^{`r round(regexp$coefficients[1],4)`+`r round(regexp$coefficients[2],4)`x}$.
Predicción: $y(30)=`r round(exp(regexp$coefficients[1] + regexp$coefficients[2]*30),4)`$ kg/m$^2$.

a. Linear coef. of determination: $r^2=`r round(r2xy,4)`$  
Logarithmic coef. of determination: $r^2=`r round(r2logxy,4)`$  
Exponential coef. of determination: $r^2=`r round(r2xlogy,4)`$  
Therefore the prediction of the logarithmic model is more reliable sinde the logarithmic coef. of determination is greater.

Meta-information 
================
extype: num
exsolution: Solution
exname: regnol-fis-2
extol: 0.001
degree: Physiotherapy
 
