
```{r echo=FALSE, results="hide"}
## DATA GENERATION
library(knitr)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
x <- c(25, 29, 32, 35, 38, 40, 43, 45, 47)
y <- c(282, 846, 2798, 7818, 14557, 20630, 31481, 37558, 43103)
z <- c(1, 25, 80, 170, 304, 425, 637, 812, 1017)
table <- matrix(c(x,y), nrow = 2, byrow = T)
# decimals <- matrix(c(rep(0,6), rep(2,6)), nrow = 3, ncol=6, byrow=TRUE)
rownames(table) <- c("Days", "Infections")
## QUESTION/ANSWER GENERATION
# colors  
col1 <- "#05A1E6"
# Sample size
n <- length(x)
# Means
mx <- mean(x)
mlogx <- mean(log(x))
my <- mean(y)
mlogy <- mean(log(y))
# Variances
s2x <- sum(x^2)/n-mx^2
s2logx <- sum(log(x)^2)/n-mlogx^2
s2y <- sum(y^2)/n-my^2
s2logy <- sum(log(y)^2)/n-mlogy^2
# Covariances
sxy <- sum(x * y) / n - mx * my
sxlogy <- sum(x*log(y))/n-mx*mlogy
slogxy <- sum(log(x)*y)/n-mlogx*my
# Determination coeff
r2xy <-  sxy^2 / (s2x * s2y)
r2xlogy <- sxlogy^2/(s2x*s2logy)
r2logxy <- slogxy^2/(s2logx*s2y)
r2yz <- cor(y,z)^2
# Linear regression model
reglin <- lm(y ~ x)
# Exponential regression model
regexp <- lm(log(y)~x)
# Regression line deaths on infections
reglinzy <- lm(z~y)
reglinyz <- lm(y~z)
```

Question
========
The table below shows the evolution of the number of coronavirus infections since the virus was detected.
```{r echo=FALSE}
kable(table) %>% kable_styling()
```


a. Which regression model, the linear or the exponential, is better to predict the number of coronavirus infections with time?

a. According to the best of the two previous regression models, how many infections will there be after 100 days? Is this prediction reliable?

a. If he number of deaths from coranvirus is linearly related to the number of infections, with a linear coefficient of determination $`r round(r2yz, 2)`$, how much will increase or decrease the number of infections for each death more if it is know that the number of deaths increases $`r round(reglinzy$coefficients[2],3)`$ for each infection more.  


Use the following sums for the computations:  
$\sum x_i=`r round(sum(x), 4)`$ days, $\sum \log(x_i)=`r round(sum(log(x)), 4)`$ $\log(\mbox{days})$, $\sum y_j=`r round(sum(y), 4)`$ infections, $\sum \log(y_j)=`r round(sum(log(y)), 4)`$ $\log(\mbox{infections})$,  
$\sum x_i^2=`r round(sum(x^2), 4)`$ days$^2$, $\sum \log(x_i)^2=`r round(sum(log(x)^2), 4)`$ $\log(\mbox{days})^2$, $\sum y_j^2=`r round(sum(y^2), 4)`$ infections$^2$, $\sum \log(y_j)^2=`r round(sum(log(y)^2), 4)`$ $\log(\mbox{infections})^2$,  
$\sum x_iy_j=`r round(sum(x*y), 4)`$ days$\cdot$infections, $\sum x_i\log(y_j)=`r round(sum(x*log(y)), 4)`$ days$\cdot\log(\mbox{infections})$, $\sum \log(x_i)y_j=`r round(sum(log(x)*y), 4)`$ $\log(\mbox{days})$infections, $\sum \log(x_i)\log(y_j)=`r round(sum(log(x)*log(y)), 4)`$ $\log(\mbox{days})\log(\mbox{infections})$.

Solution
========

a. $\bar x=`r round(mx,4)`$ days, $s_x^2=`r round(s2x,4)`$ days$^2$.  
$\bar y=`r round(my,4)`$ infections, $s_y^2=`r round(s2y,4)`$ infections$^2$.  
$\overline{\log(y)}=`r round(mlogy,4)`$ log(infections), $s_{\log(y)}^2=`r round(s2logy,4)`$ log(infections)$^2$.  
$s_{xy}=`r round(sxy,4)`$ days$\cdot$infections, $s_{x\log(y)}=`r round(sxlogy,4)`$ days$\cdot\log(infections)$.  
Linear coefficient of determination: $r^2=`r round(r2xy,4)`$  
Exponential coefficient of determination: $r^2=`r round(r2xlogy,4)`$  
Thus, the exponential model is better to predict the number of infections since its coefficient of determination is greater.

a. Exponential regression model: $y=e^{`r round(regexp$coefficients[1],4)`+`r round(regexp$coefficients[2],4)`x}$.  
Prediction: $y(100)=`r round(exp(regexp$coefficients[1] + regexp$coefficients[2]*100),4)`$ infections. The prediction is not reliable because 100 days is far away from the range of days in the sample.

a. According to the regression coefficient, ther will be $`r round(reglinyz$coefficients[2],3)`$ infections more for each death more. 

Meta-information 
================
extype: num
exsolution: Solution
exname: regnol-med-7
extol: 0.001
degree: Physiotherapy
 
