
```{r echo=FALSE, results=hide}
## DATA GENERATION
library(kntir)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
x <- c(10, 14, 8, 11, 7, 6, 2, 5, 9, 9, 4, 6)
y <- c(2.55, 2.44, 2.68, 2.65, 2.71, 2.85, 3.45, 2.93, 2.67, 2.59, 3.02, 2.72)
table <- matrix(c(x,y), nrow = 2, byrow = T)
rownames(table) <- c("Daily num cigarettes", "Weight (kg)")
## QUESTION/ANSWER GENERATION
# colors
col1 <- "#05A1E6"
# sample size
n <- length(x)
# means
mx <- mean(x)
mlogx <- mean(log(x))
my <- mean(y)
mlogy <- mean(log(y))
# variances
s2x <- sum(x^2)/n-mx^2
s2logx <- sum(log(x)^2)/n-mlogx^2
s2y <- sum(y^2)/n-my^2
s2logy <- sum(log(y)^2)/n-mlogy^2
# Covariances
sxy <- sum(x*y)/n-mx*my
sxlogy <- sum(x*log(y))/n-mx*mlogy
slogxy <- sum(log(x)*y)/n-mlogx*my
# Determination coeff
r2xy <- sxy^2/(s2x*s2y)
r2xlogy <- sxlogy^2/(s2x*s2logy)
r2logxy <- slogxy^2/(s2logx*s2y)
# Linear regression model
reglin <- lm(y~x)
# Exponential regression model
regexp <- lm(log(y)~x)
# Logarithmic regression model
reglog <- lm(y~log(x))
```

Question
========
A study tries to determine the effect of smoking during the pregnancy in the weight of newborns. The table below shows the daily number of cigarretes smoked by mothers ($X$) and the weight of the newborn (all of them are males) ($Y$).

```{r echo=FALSE}
kable(table) %>% kable_styling()
```

a. Give the equation of the regression line of the weight of newborns on the daily number of cigarettes and interpret the slope.
a. Which regression model is better to predict the weight of newborns, the  logarithmic or the exponential?
a. Use the best of the two previous regression models to predict the weight of a newborn whose mother smokes 12 cigarettes a day. Is this prediction reliable?

Use the following sums for the computations:  
$\sum x_i=`r round(sum(x), 4)`$ cigarettes, $\sum \log(x_i)=`r round(sum(log(x)), 4)`$ $\log(\mbox{cigarettes})$, $\sum y_j=`r round(sum(y), 4)`$ kg, $\sum \log(y_j)=`r round(sum(log(y)), 4)`$ $\log(\mbox{kg})$,  
$\sum x_i^2=`r round(sum(x^2), 4)`$ cigarettes$^2$, $\sum \log(x_i)^2=`r round(sum(log(x)^2), 4)`$ $\log(\mbox{cigarettes})^2$, $\sum y_j^2=`r round(sum(y^2), 4)`$ kg$^2$, $\sum \log(y_j)^2=`r round(sum(log(y)^2), 4)`$ $\log(\mbox{kg})^2$,  
$\sum x_iy_j=`r round(sum(x*y), 4)`$ cigarettes$\cdot$kg, $\sum x_i\log(y_j)=`r round(sum(x*log(y)), 4)`$ cigarettes$\cdot\log(\mbox{kg})$, $\sum \log(x_i)y_j=`r round(sum(log(x)*y), 4)`$ $\log(\mbox{cigarettes})$kg, $\sum \log(x_i)\log(y_j)=`r round(sum(log(x)*log(y)), 4)`$ $\log(\mbox{cigarettes})\log(\mbox{kg})$.

Solution
========
a. $\bar x=`r round(mx,4)`$ cigarettes, $s_x^2=`r round(s2x,4)`$ cigarettes$^2$.  
$\bar y=`r round(my,4)`$ kg, $s_y^2=`r round(s2y,4)`$ kg$^2$.  
$s_{xy}=`r round(sxy,4)`.$ cigarettes$\cdot$kg  
Regression line: $y=`r round(reglin$coefficients[2],4)`x + `r round(reglin$coefficients[1],4)`$.
a. $\overline{\log(x)}=`r round(mlogx,4)`$ log(cigarettes), $s_{\log(x)}^2=`r round(s2logx,4)`$ log(cigarettes)$^2$.  
$\overline{\log(y)}=`r round(mlogy,4)`$ log(kg), $s_{\log(y)}^2=`r round(s2logy,4)`$ log(kg)$^2$.  
$s_{x\log(y)}=`r round(sxlogy,4)`$ cigarettes$\cdot$log(kg), $s_{\log(x)y}=`r round(slogxy,4)`$ log(cigarettes)$\cdot$kg  
Logarithmic coef. determination: $r^2=`r round(r2logxy,4)`$  
Exponential coef. determination: $r^2=`r round(r2xlogy,4)`$  
Therefore, the logarithmic models fits better the data and is better to predict the weight.
a. Logarithmic regression model: $y=`r round(reglog$coefficients[1],4)`+`r round(reglog$coefficients[2],4)`\log(x)$.  
Prediction: $y(12)=`r round(reglog$coefficients[1]+reglog$coefficients[2]*log(12), 4)`$ kg.
The coefficient of determination is high but the sample size small, so the prediction is not enterely reliable.

Meta-information 
================
extype: num
exsolution: Solution
exname: regnol-fis-4
extol: 0.001
degree: Physiotherapy
 
