
```{r echo=FALSE, results=hide}
## DATA GENERATION
library(kntir)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(kableExtra)
x <- c(2015, 2016, 2017, 2018, 2019)
y <- c(1.4, 1.6, 1.92, 2.3, 2.91)
table <- matrix(c(x,y), nrow = 2, byrow = T)
decimals <- matrix(c(rep(0,6), rep(2,6)), nrow = 2, ncol=6, byrow=TRUE)
rownames(table) <- c("Year", "Price (€)")
## QUESTION/ANSWER GENERATION
# colors
col1 <- "#05A1E6"
# sample size
n <- length(x)
# means
mx <- mean(x)
mlogx <- mean(log(x))
my <- mean(y)
mlogy <- mean(log(y))
# variances
s2x <- sum(x^2)/n-mx^2
s2logx <- sum(log(x)^2)/n-mlogx^2
s2y <- sum(y^2)/n-my^2
s2logy <- sum(log(y)^2)/n-mlogy^2
# Covariances
sxy <- sum(x * y) / n - mx * my
sxlogy <- sum(x*log(y))/n-mx*mlogy
slogxy <- sum(log(x)*y)/n-mlogx*my
# Determination coeff
r2xy <-  sxy^2 / (s2x * s2y)
r2xlogy <- sxlogy^2/(s2x*s2logy)
r2logxy <- slogxy^2/(s2logx*s2y)
# Linear regression model
reglin <- lm(y ~ x)
# Exponential regression model
regexp <- lm(log(y)~x)
# Logarithmic regression model
reglog <- lm(y~log(x))
```

Question
========
The evolution of the price of a muscle relaxant between 2015 and 2019 is shown in the table below.

```{r echo=FALSE}
kable(table) %>% kable_styling()
```

a. Which regression model is better to predict the price, the linear or the exponential?
a. Use the best of the two previous models to predict the price in 2020.


Use the following sums for the computations:  
$\sum x_i=`r round(sum(x), 4)`$ cigarros, $\sum \log(x_i)=`r round(sum(log(x)), 4)`$ $\log(\mbox{cigarros})$, $\sum y_j=`r round(sum(y), 4)`$ kg, $\sum \log(y_j)=`r round(sum(log(y)), 4)`$ $\log(\mbox{kg})$,  
$\sum x_i^2=`r round(sum(x^2), 4)`$ cigarros$^2$, $\sum \log(x_i)^2=`r round(sum(log(x)^2), 4)`$ $\log(\mbox{cigarros})^2$, $\sum y_j^2=`r round(sum(y^2), 4)`$ kg$^2$, $\sum \log(y_j)^2=`r round(sum(log(y)^2), 4)`$ $\log(\mbox{kg})^2$,  
$\sum x_iy_j=`r round(sum(x*y), 4)`$ cigarros$\cdot$kg, $\sum x_i\log(y_j)=`r round(sum(x*log(y)), 4)`$ cigarros$\cdot\log(\mbox{kg})$, $\sum \log(x_i)y_j=`r round(sum(log(x)*y), 4)`$ $\log(\mbox{cigarros})$kg, $\sum \log(x_i)\log(y_j)=`r round(sum(log(x)*log(y)), 4)`$ $\log(\mbox{cigarros})\log(\mbox{kg})$.

Solution
========
a. $\bar x=`r round(mx,4)`$ years, $s_x^2=`r round(s2x,4)`$ years$^2$.  
$\bar y=`r round(my,4)`$ €, $s_y^2=`r round(s2y,4)`$ €$^2$.  
$\overline{\log(y)}=`r round(mlogy,4)`$ log(€), $s_{\log(y)}^2=`r round(s2logy,4)`$ log(€)$^2$.  
$s_{xy}=`r round(sxy,4)`$, $s_{x\log(y)}=`r round(sxlogy,4)`$  
Linear coef. determination: $r^2=`r round(r2xy,4)`$  
Exponential coef. determination: $r^2=`r round(r2xlogy,4)`$  
Thus the exponential regression model is better to predict the price since the coef. of determination is greater.
a. Exponential regression model: $y=e^{`r round(regexp$coefficients[1],4)`+`r round(regexp$coefficients[2],4)`x}$.  
Prediction: $y(2020)=`r round(exp(regexp$coefficients[1] + regexp$coefficients[2]*2020),4)`$ €.

Meta-information 
================
extype: num
exsolution: Solution
exname: regnol-fis-4
extol: 0.001
degree: Physiotherapy
 
