
```{r echo=FALSE, results=hide}
## DATA GENERATION
pC <- 0.08
pHsiC <- 0.040
pCsiH <- 0.1
## QUESTION/ANSWER GENERATION
pCH <- 0.0032
pCnoH <- 0.0768
pnoCH <- 0.0288
pnoCnoH <- 0.8912
rC <- pCH / (pCH + pCnoH)
rnoC <- pnoCH / (pnoCH + pnoCnoH)
rr <- rC / rnoC
oC <- pCH / pCnoH
onoC <- pnoCH / pnoCnoH
or <- oC / onoC
```
```{r tikzsource, echo=FALSE, results = hide}
typ <- match_exams_device()
graf01 <- "
\\begin{tikzpicture}[
grow'=right,
% sloped,
level 1/.style ={level distance=2cm, sibling distance=1.6cm, parent anchor=east, child anchor=west},
level 2/.style ={level distance=2cm, sibling distance=0.8cm},
level 3/.style ={level distance=1.5cm, sibling distance=0.8cm, dashed},
level 4/.style ={level distance=3cm, sibling distance=0.8cm, dashed},
prob/.style={font=\\footnotesize,above}
]


\\node (root) {}
	child {node {$C$}
		child {node {$H$}
			child {node{$C\\cap H$}
				child {node{$0.0032$} edge from parent node[prob] {$0.08\\cdot 0.04$}}
			}
			edge from parent node[prob] {$0.04$}
		}
		child {node {$\\overline{H}$}
			child {node{$C\\cap \\overline{H}$}
				child {node{$0.0768$} edge from parent node[prob] {$0.08\\cdot 0.96$}}
			}
			edge from parent node[prob,below] {$0.96$}
		}
		edge from parent node[prob] {$0.08$}
	}
	child {node {$\\overline{C}$}
   		child {node {$H$}
			child {node{$\\overline{C}\\cap H$} 
				child {node{$0.0288$} edge from parent node[prob] {$0.92\\cdot 0.0313$}}
			}
			edge from parent node[prob] {$0.0313$}
		}
		child {node {$\\overline{H}$}
			child {node{$\\overline{C}\\cap\\overline{H}$} 
				child {node{$0.8912$} edge from parent node[prob] {$0.92\\cdot 0.9687$}}
			}
			edge from parent node[prob,below] {$0.9687$}
		}
		edge from parent node[prob,below] {$0.92$}
	};

\\begin{scope}[every node/.style={text width=2cm, align=center, anchor=center, font=\\bfseries,}]
\\node[above= 0.5cm of root-1-1-1-1] (labels-level) {Probability};
\\node[at =(labels-level-|root-1-1-1)] {$\\Omega$};
\\node[at =(labels-level-|root-1-1)] {Heart attack};
\\node[at =(labels-level-|root-1)] {Cocaine};
\\end{scope}
\\end{tikzpicture}
"
```

Question
========
	
8%: of people in a population consume cocaine. It is also known that 4%: of people who consume cocaine have a heart attack and 10%: of people who have a heart attack consume cocaine.

a. Construct the probability tree for the random experiment of drawing a random person from the population and measuring if he or she consumes cocaine and if he or she has a heart attack.
a. Compute the probability that a random person of the population does not consume cocaine and does not have a heart attack.
a. Are the events of consuming cocaine and having a heart attack dependent?
a. Compute the relative risk and the odds ratio of suffering a heart attack consuming cocaine. Which association measure is more suitable for this study? Interpret it.

Solution
========
Let $C$ the event of consuming cocaine and $H$ the event of having a heart attack.
a. 
```{r tree, echo = F}
include_tikz(graf01, name = "graf", format = typ, markup = "tex", library = "positioning", width = "7cm")
```

a. $P(\overline C\cap \overline H)=`r round(pnoCnoH, 4)`$.
a. The events are dependent as $P(C)=`r pC`\neq P(C|H)=`r pCsiH`$.
a. $RR(H)=`r round(rr, 4)`$ and $OR(H)=`r round(or, 4)`$. The odds ratio is more suitable as the study is retrospective. That means that the odds of having a heart attack is $`r round(or, 4)`$ times greater if a person consumes cocaine.

Meta-information 
================
extype: num
exsolution: Solution
exname: ries-5-med
extol: 0.001
degree: Medicine
 
