
```{r echo=FALSE, results="hide"}
## DATA GENERATION
x <- c(20, 22.5, 25, 27.5, 30, 32.5, 35, 37.5, 40)
y <- c(2.3, 2, 2, 1.8, 2.2, 1.5, 1.2, 1.3, 0.6)
table <- matrix(c(x,y), nrow = 2, byrow = T)
decimals <- matrix(rep(1,18), nrow = 2, ncol=9, byrow=TRUE)
rownames(table) <- c("Salary", "Absences")
sumx <- sum(x)
sumy <- sum(y)
sumx2 <- sum(x^2)
sumy2 <- sum(y^2)
sumxy <- sum(x*y)
n <- length(x)
  
## QUESTION/ANSWER GENERATION
# means
mx <- sumx / n
my <- sumy / n
# variances
s2x <- sumx2/n-mx^2
s2y <- sumy2/n-my^2
# Covariances
sxy <- sumxy/n-mx*my
# Detercmation coeff
r2 <- sxy^2/(s2x*s2y)
# Regression line
lm <- lm(y~x)
```

Question
========
An auditor is studying the relationship between the salary and the number of absences of a hospital warden. The following table shows the salary in thousands of euros ($X$) and the annual average of absences with that salary ($Y$).

```{r echo=FALSE}
kable(table) %>% kable_styling()
```


a. Compute the regression line that best explains the absences as a function of the salary.

a. What is the expected number of absences that will have a warden with a salary of 29000€? Is this prediction reliable?

a. How much will the number of absences increase or decrease for every increment of 1000€ in the salary?

Use the following sums for the computations:  
$\sum x_i=`r sumx`$ $10^3$€, $\sum y_i=`r sumy`$ absences,  
$\sum x_i^2=`r sumx2`$ ($10^3$€)$^2$, $\sum y_i^2=`r sumy2`$ absences$^2$,  
$\sum x_iy_j=`r sumxy`$ $10^3$€ absences.

Solution
========

a. $\bar x=`r round(mx,4)`$ $10^3$€, $s_x^2=`r round(s2x,4)`$ ($10^3$€)$^2$,  
$\bar y=`r round(my,4)`$ absences, $s_y^2=`r round(s2y,4)`$ absences$^2$,  
$s_{xy}=`r round(sxy,4)`$ $10^3$€ absences.  
Regression line of absences on salary: $y=`r round(lm$coefficients[1], 4)`   `r round(lm$coefficients[2], 4)`x$.

a. $y(29) = `r round(lm$coefficients[1] + lm$coefficients[2]*29, 4)`$ absences.  
$r^2 = `r round(r2, 4)`$, thus the model fits well as the coefficient of determination is not far from 1, but the sample size is too small to be reliable the prediction.

a. The number of absences will decrease `r round(abs(lm$coefficients[2]), 4)` for every increment of 1000€ in the salary.

Meta-information 
================
extype: num
exsolution: Solution
exname: reglin-far-11
extol: 0.001
degree: Pharmacy
 
