
```{r echo=FALSE, results=hide}
## DATA GENERATION
  x <- c(20,40,60)
  y <- c(42,40,38)
  y2 <- c(44,40,36)
  df <- data.frame(x,y,y2)
## QUESTION/ANSWER GENERATION
```

Question
========
The relationship between basal metabolic rate and age is being studied in a sample of healthy men and the following regression lines have been obtained
```{r regression-lines, fig=T, echo=F, height=4, width=6, dev="svg", fig.path="img"}
plot(x, y, type="n", ylim = c(34,45), yaxt = "n", xlab="Age", ylab="Basal metabolic rate") 
axis(1, at = seq(20,60,5), tck = 1, lty = 2, col = "gray")
axis(2, at = 34:45, tck = 1, lty = 2, col = "gray")
box()
lines(x, y, col = "blue")
lines(x, y2, col = "blue")
```

a. Compute the means of the basal metabolic rate and the age.
a. How is the fit of the two lines?

Solution
========
Let $X$ be the age and $Y$ the basal metabolic rate.
a. $\bar x=40$ and $\bar y=40$.
a. $b_{yx}=-0.1$, $b_{xy}=-5$ and $r^2 = 0.5$, thus the fit of the regression lines moderate.

Meta-information 
================
extype: num
exsolution: Solution
exname: reglin-16-nut
extol: 0.001
%% \degree{Nutrition}
 
