
```{r echo=FALSE, results="hide"}
## DATA GENERATION
x <- c(5.5, 7.5, 2.5, 6, 8, 4, 7, 9.5, 10, 1)
y <- c(3.2, 6.5, 4, 4, 7.5, 3.5, 5.5, 10, 9.5, 3)
z <- c(5, 2, 1, 6, 6, 1, 4, 9, 8, 0.5)
data <- data.frame(x, y, z)
colnames(data) <- c("Exam 1 (X)", "Exam 2 (Y)", "Exam 3 (Z)")

## QUESTION/ANSWER GENERATION
n <- length(x)
# means
mx <- sum(x) / n
my <- sum(y) / n
mz <- sum(z) / n
# variances
s2x <- sum(x^2)/n-mx^2
s2y <- sum(y^2)/n-my^2
s2z <- sum(z^2)/n-mz^2
# Covariances
sxy <- sum(x*y)/n-mx*my
syz <- sum(y*z)/n-my*mz
sxz <- sum(x*z)/n-mx*mz
# Determination coeff
r2xy <- sxy^2/(s2x*s2y)
r2xz <- sxz^2/(s2x*s2z)
r2yz <- syz^2/(s2y*s2z)
# Regression lines
lyx <- lm(y~x)
lzx <- lm(z~x)
predy <- lyx$coefficients[1]+lyx$coefficients[2]*6.5
predz <- lzx$coefficients[1]+lzx$coefficients[2]*6.5
```

Question
========
The table below summarizes the scores of a group of 10 students in three practical exams of Maths.
```{r echo=FALSE}
kable(data) %>% kable_styling()
```
  

a. Which two scores are more linearly correlated?

a. Using linear models, what are the expected scores of the second and third exams for a student with a score $6.5$ in the first exam?


Use the following sums for the computations:  
$\sum x_i=`r sum(x)`$, $\sum y_i=`r sum(y)`$, $\sum z_i=`r sum(z)`$,  
$\sum x_i^2=`r sum(x^2)`$, $\sum y_i^2=`r sum(y^2)`$, $\sum z_i^2=`r sum(z^2)`$,  
$\sum x_iy_j=`r sum(x*y)`$, $\sum x_iz_j=`r sum(x*z)`$, $\sum y_jz_j=`r sum(y*z)`$.

Solution
========

a. $\bar x=`r round(mx,4)`$, $s_x^2=`r round(s2x,4)`$,  
$\bar y=`r round(my,4)`$, $s_y^2=`r round(s2y,4)`$,  
$\bar z=`r round(mz,4)`$, $s_z^2=`r round(s2z,4)`$,  
$s_{xy}=`r round(sxy,4)`$, $s_{xz}=`r round(sxz,4)`$, $s_{yz}=`r round(syz,4)`$,  
$r^2_{xy}=`r round(r2xy,4)`$, $r^2_{xz}=`r round(r2xz,4)`$ and $r^2_{yz}=`r round(r2yz,4)`$.  
Thus, the two variables more linearly related are $X$ and $Y$, since their coefficient of determination is greater.

a. Regression line of $Y$ on $X$: $y=`r round(lyx$coefficients[1],4)` + `r round(lyx$coefficients[2],4)`x$ and $y(6.5)=`r round(predy, 4)`$.  
Regression line of $Z$ on $X$: $z=`r round(lzx$coefficients[1],4)` + `r round(lzx$coefficients[2],4)`x$ and $z(6.5)=`r round(predz, 4)`$.

Meta-information 
================
extype: num
exsolution: Solution
exname: reglin-far-8
extol: 0.001
degree: Pharmacy
 
