\begin{enumerate}
\item
  \textbf{Question}\\
  The temperature of a gel depends on time according to the function
  \(T(x)=x^2+\ln(1.5-x)\), where \(T\) is the temperature in degrees
  Celsius and \(x\) is the time in hours.

  \begin{enumerate}
  \item
    Compute the minimum and maximum temperature of the gel in the
    interval from 0 to 1.5 hours?
  \item
    How fast is the temperature changing at 1.2 hours? Compute
    approximately the value of the temperature 5 minutes after using the
    tangent line.
  \item
    At what time is the rate of change of temperature maximum?
  \end{enumerate}

  \textbf{Solution}\\
\item
  \textbf{Question}\\
  A dialysis machine works under the principle of Fick's Law, which
  states that the amount of waste material that passes through a
  membrane is proportional to the difference between the concentration
  of one side and the other of it. At the start of dialysis, the waste
  material concentration of a patient is 160 mg/dl and after 1 hour it
  drops to half, while the dialysate solution at the other side of the
  membrane remains at a constant concentration of 10 mg/dl. If dialysis
  finish when the patient reaches a concentration of 20 mg/dl, how long
  will the patient have to be on dialysis to get it?

  \textbf{Solution}\\
\item
  \textbf{Question}\\
  In a pharmacy, the amount of paracetamol \(Q\) demanded by customers
  depends on the price of paracetamol \(p\) and the price of ibuprofen
  \(b\), according to the function

  \[Q(p,b) = \frac{6b}{(p-1)p}\]

  \begin{enumerate}
  \item
    For which values of \(p\) and \(b\) this function make sense in this
    context?
  \item
    If the price of paracetamol increases, will the demand for
    paracetamol increase or decrease?
  \item
    If the prices of paracetamol and ibuprofen are \(p=2\) and \(b=1\)
    €, how should the prices of paracetamol and ibuprofen vary so that
    the quantity demanded of paracetamol increases as much as possible?
  \item
    Assuming the same prices as in the previous question, how much will
    the quantity of paracetamol demanded change if the price of
    paracetamol increases half of ibuprofen price increase?
  \end{enumerate}

  \textbf{Solution}\\
\end{enumerate}
