\begin{enumerate}
\item
  \textbf{Question}\\
  To analyze the hypoxemia tolerance of mammals, in a laboratory some
  rats are exposed to extreme conditions with variable levels of oxygen.
  The rats are in a room whose oxygen level (in \%) at any position
  \((x,y)\) is

  \[O(x,y)=\frac{1}{10}x^2y^2e^{x-y}\]

  For the rats to survive, they must reach positions where the oxygen
  level is above 18\%.

  \begin{enumerate}
  \item
    A rat \(A\) is at position \((3,2)\). If the rat stays in that
    position, will it survive?
  \item
    What direction should rat \(A\) take in order to increase the oxygen
    level as quickly as possible? What is the instantaneous rate of
    change of the oxygen level following that direction?
  \item
    Another rat \(B\) is at position \((2,2)\). If it starts to move in
    such a way that \(y\) decreases the double of the increment of
    \(x\), how will the oxygen level change?
  \end{enumerate}

  \textbf{Solution}\\
\item
  \textbf{Question}\\
  The ozone (\(O_3\)) in the atmosphere is transformed into oxygen
  (\(O_2\)) through the following chemical reaction:

  \[2O_3 \rightarrow 3O_2\]

  It was experimentally observed that the speed at which the amount of
  oxygen varies is inversely proportional to the amount of oxygen
  present. If there is initially 10 g of oxygen in a place, and after
  one hour this amount of oxygen doubles,

  \begin{enumerate}
  \item
    What will the amount of oxygen be after 5 hours?
  \item
    How long will it take to have 1 kg of oxygen?
  \end{enumerate}

  \textbf{Solution}\\
\item
  \textbf{Question}\\
  Two insects start moving from the same point following perpendicular
  directions.

  \begin{enumerate}
  \item
    If the first insect moves at a speed of 3 cm/s and the second at a
    speed of 4 cm/s, at what instantaneous speed does the distance
    between them change 2 seconds after they start moving? And at 3
    seconds?
  \item
    If 4 seconds after they start moving the second insect stops and the
    first continues moving with the same direction and speed, at what
    instantaneous speed does the distance between the two insects change
    at that moment?
  \end{enumerate}

  Remark: The distance between the two insects is the length of the
  hypotenuse of the right triangle whose sides are the distance traveled
  by them.

  \textbf{Solution}\\
\end{enumerate}
